\section{Discussion}

The main lesson is geometric and local.  We are not proving that spectral data
globally determine shell shape, nor even that every non-spherical perturbation
helps.  We are showing that, for the present five-mode inverse map, the
recoverability of $(a,c,E)$ depends strongly on \emph{which} geometry family is
used to leave the spherical limit.  The difference between
$\kappa_\mathrm{oblate}=\num{69.4}$ and $\kappa_\mathrm{prolate}=156$ is too
large to dismiss as a numerical quirk.

A plausible physical interpretation is mode-dependent curvature sampling.  In the Ritz
model, different flexural modes weight the equatorial and polar regions
differently in the strain-energy integrals.  Oblate deformation redistributes
curvature in a way that makes the $a$- and $c$-sensitivity columns less nearly
parallel, so the smallest singular value grows.  The equivalent-sphere reduction
suppresses that mechanism completely because both geometric variables are routed
through $R_\mathrm{eq}$ alone.  The prolate family preserves the formal break
from spherical symmetry but does not generate an equally useful separation of
sensitivity directions.

This asymmetry also clarifies the relation between the companion papers.
Paper~1 motivates the abdominal shell as an oblate, fluid-loaded structure whose
low-order flexural modes sit in the infrasonic band \cite{BrowntoneP1}.  Paper~7
shows why an equivalent-sphere model can still be serviceable when the
engineering question is dominated by one effective stiffness scale
\cite{BrowntoneP7}.  Paper~8 demonstrates that the moment one asks for joint
recovery of geometry and material parameters, that reduction can become the
problem rather than the cure \cite{BrowntoneP8}.  The present calculations show
that this loss of information is relieved more effectively by oblate than by
prolate curvature redistribution.

Several limits should be kept in view.  The analysis is local, based on the
Jacobian at a chosen operating point.  It uses five low-order flexural modes,
not a complete spectrum.  It is tied to the present shell parameterisation and
to the fluid-loaded Ritz formulation grounded in classical shell and
fluid--structure theory \cite{Lamb1882,JungerFeit1986}.  None of this implies
that prolate bodies are unrecoverable under all measurements, only that the
current spectral map does not improve appreciably when the geometry is made
prolate.  If such cases must be inverted, additional observables or external
priors will be required.
