\documentclass[review]{elsarticle}
\usepackage[margin=1in]{geometry}

% =============================================================================
% Packages
% =============================================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{inconsolata}
\usepackage{amsmath}
\let\Bbbk\relax
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{lineno}

% Fix duplicate page destination warning with elsarticle review mode
\hypersetup{pageanchor=false}
\AtBeginDocument{\hypersetup{pageanchor=true}}

% SI units configuration
\sisetup{
  per-mode=symbol,
  group-separator={,},
}

% Line numbering (required for review submission)
\linenumbers

% =============================================================================
% Metadata
% =============================================================================
\journal{Inverse Problems}

\begin{document}

\begin{frontmatter}

\title{Can You Hear the Shape of an Organ? Practical Identifiability of
Viscoelastic Shell Parameters from Resonant Frequencies}

\author[msr]{Jonathan Mace\corref{cor1}}
\cortext[cor1]{Corresponding author}
\ead{jonathanmace@microsoft.com}

\author[auckland]{Brian R.\ Mace}
\ead{br.mace@auckland.ac.nz}

\affiliation[msr]{
  organization={Microsoft Research},
  city={Redmond, WA},
  country={United States}
}

\affiliation[auckland]{
  organization={Acoustics Research Centre, Department of Mechanical and
    Mechatronics Engineering, University of Auckland},
  city={Auckland},
  country={New Zealand}
}

\begin{abstract}
We investigate the practical identifiability of material and geometric
parameters of a fluid-filled viscoelastic oblate spheroidal shell from its
resonant frequencies --- the inverse counterpart of Kac's celebrated question
``Can one hear the shape of a drum?'' applied to vibroacoustic organ models.
Using a Rayleigh--Ritz forward model for flexural vibrations, we compute the
Jacobian of the frequency--parameter map, its condition number, and the Fisher
information matrix.  For a sphere, the Jacobian is rank-deficient (condition
number $\sim 10^{10}$) because all flexural modes scale identically with the
equivalent radius: geometry and stiffness are confounded.  For an oblate
spheroid, different modes sample the anisotropic curvature differently,
yielding a full-rank Jacobian (condition number $\approx 83.5$) and
finite Cram\'er--Rao bounds.  We demonstrate sub-percent parameter recovery
via Newton--Raphson inversion from three modal frequencies under realistic
noise.  The result has implications for non-invasive tissue characterisation:
one can ``hear the shape'' of an oblate organ, but not a spherical one.
\end{abstract}

\begin{keyword}
inverse problem \sep identifiability \sep viscoelastic shell \sep
resonant frequency \sep condition number \sep Cram\'er--Rao bound \sep
oblate spheroid \sep Kac problem
\end{keyword}

\end{frontmatter}

% =============================================================================
% Graphics path
% =============================================================================
\graphicspath{{../figures/}}

% =============================================================================
% Body
% =============================================================================

% --- Introduction ---
\input{sections/introduction}

% --- Theory ---
\input{sections/theory}

% --- Methodology ---
\input{sections/methodology}

% --- Results ---
\input{sections/results}

% --- Discussion ---
\input{sections/discussion}

% --- Conclusion ---
\input{sections/conclusion}

% =============================================================================
% References
% =============================================================================
\bibliographystyle{elsarticle-num}
\bibliography{references}

% =============================================================================
% Back matter
% =============================================================================

\section*{Data availability}
All code and data required to reproduce the results are available in the
accompanying repository at \url{https://github.com/JonathanMace/brownnote}.

\section*{CRediT authorship contribution statement}
\textbf{Jonathan Mace}: Conceptualisation, Methodology, Software,
Writing -- Original Draft.
\textbf{Brian R.\ Mace}: Supervision, Writing -- Review \& Editing.

\section*{Acknowledgements}
The authors gratefully acknowledge the support of Microsoft Research
and the University of Auckland Acoustics Research Centre.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests
or personal relationships that could have appeared to influence the work
reported in this paper.

\end{document}
