% =============================================================================
% Section 5 — Conclusions
% =============================================================================
\section{Conclusions}
\label{sec:conclusions}

We have extended the fluid-filled viscoelastic oblate spheroidal shell
model of Mace and Mace~\cite{Mace2026browntone} to the sub-bass band
(\SIrange{20}{80}{\hertz}) and performed a quantitative pathway partition
of the ``feel it in your gut'' experience at concert sound pressure
levels.  The principal findings are:
%
\begin{enumerate}
  \item The Helmholtz number $ka$ increases from $0.011$ at
    \SI{3.95}{\hertz} to $0.23$ at \SI{80}{\hertz}, improving the
    acoustic coupling factor $(ka)^2$ by up to ${\sim}400\times$.

  \item This improvement is largely offset by the off-resonance
    attenuation of the SDOF transfer function: at \SI{40}{\hertz}
    ($r \approx 10$), $H \approx 0.01$.

  \item Using the energy-consistent Junger \& Feit reciprocity
    formulation, airborne-induced tissue displacement at peak EDM levels
    (\SI{115}{\decibel} at \SI{40}{\hertz}) reaches
    $\sim$\SI{0.35}{\percent} of the whole-body vibration perception
    threshold---a near-miss, approximately \num{2.5}~orders of magnitude
    below threshold.

  \item The structure-borne (floor/seat) pathway dominates the airborne
    pathway by a factor of $\sim$\num{2600}
    (90\% CI: \numrange{2000}{3100}), reaching $\sim 9\times$ the
    perception threshold at peak EDM levels (90\% CI:
    $5.8$--$12.7\times$).

  \item Near-field pressure enhancement (\SIrange{6}{10}{\decibel}
    within \SI{1.5}{\metre} of a subwoofer) narrows the airborne gap
    by a factor of $\sim$3 but does not bring it to perceptibility.

  \item Wooden church pews have first bending resonances at
    \SIrange{12}{19}{\hertz}, providing a structure-borne coupling
    path that may explain visceral sensation during pipe-organ
    performances.

  \item No ``coupling transition band'' exists in the
    \SIrange{1}{100}{\hertz} range at concert SPLs: the airborne
    displacement never exceeds \SI{1}{\percent} of the perception
    threshold at any frequency.
\end{enumerate}

These results reframe the ``feel it in your gut'' question from a binary
(can airborne sound do it?) to a quantitative pathway partition.  The
airborne contribution is not negligibly small---it is a genuine
near-miss---but the structure-borne pathway is overwhelmingly dominant.
Of the two pathways analysed, structure-borne transmission accounts for
$>{99.9}\%$ of abdominal wall displacement; however, neither pathway
alone accounts for the full visceral experience, which likely also
involves chest-wall coupling, somatosensory stimulation, and vestibular
input.  Sound engineers and venue designers seeking to maximise the
physical impact of bass should focus on structural vibration
transmission rather than acoustic levels.
The audience does not feel the bass through the air; it feels the bass
through the floor.  The distinction matters less for the musical
experience than for the acoustic engineer's budget.