% =============================================================================
% Section 6: Conclusion
% =============================================================================
% PURPOSE:
%   Restate the programme's thesis: in fluid-filled viscoelastic shells,
%   geometry does three jobs — filters forcing, organises spectra,
%   determines invertibility.
%   Summarise the four formal results and their cross-application evidence.
%   Identify open problems: extension to non-axisymmetric geometries,
%   layered walls, nonlinear regimes, and experimental validation.
%   End with a forward-looking statement on the role of geometric
%   reasoning in vibroacoustic inverse problems.
% =============================================================================

\section{Conclusion}
\label{sec:conclusion}

This paper has argued that the Browntone programme is best understood not as a
collection of curious applications, but as a coherent theory of geometry in
fluid-filled compliant shells.  The central thesis is that geometry does three
jobs.  It filters how external forcing couples into admissible shell motions; it
organises the modal spectrum through symmetry, curvature, and fluid loading; and
it determines whether the spectrum can be inverted to recover the parameters
that generated it.  That thesis emerged first from the abdominal and sub-bass
problems, broadened through bladder, gas-pocket, scaling-law, and borborygmi
studies, and reached its sharpest form in the inverse analyses of watermelon
acoustics and organ-shape identifiability~\cite{BrowntoneP1,BrowntoneP2,BrowntoneP3,BrowntoneP4,BrowntoneP5,BrowntoneP6,BrowntoneP7,BrowntoneP8}.

Within that framework, four formal results have now been established.  The
first shows that equivalent-radius reductions of non-spherical fluid-filled
shells are generically rank deficient, because they collapse independent
geometric information into a single size parameter.  The second shows that
oblate asphericity can lift that deficiency by allowing different modes to
sample curvature differently.  The third shows that the transition to the
spherical limit is a regular asymptotic problem with
$\sigma_3(\varepsilon)=\lambda_1\varepsilon^2+O(\varepsilon^4)$, so the exact
sphere is singular and the previously reported finite floor was a
discretisation artefact.  The fourth, and perhaps most consequential, is that
forward adequacy does not imply inverse adequacy.  A model may predict
frequencies well enough to look convincing while remaining unsuitable for
parameter recovery.

The cross-application evidence suggests, moreover, that identifiability lifting
is geometry selective rather than universal.  Oblate perturbations appear able
to generate the modal differentiation needed for stable inversion, whereas
prolate perturbations need not do so.  Reduced models for spectral inference
should therefore be judged not only by forward accuracy, but by whether they
preserve the geometry-induced sensitivity structure required by the inverse task.

We have been careful not to overstate what has been established.  The capstone
is analytical, not experimental.  The shell models are linear, thin, and
intentionally reduced.  Even so, the present paper now places the central
inverse claims on theorem, proposition, and lemma level within that reduced
class.  A sufficiently consistent picture has therefore emerged to support a
broader claim: spectral mechanics in fluid-filled compliant enclosures can be
organised around geometry as an information-bearing structure, rather than
treated as a collection of isolated frequency calculations.

That perspective offers a template for future work in biomechanics, biomedical
sensing, non-destructive testing, and industrial noise, vibration, and harshness.
Wherever one seeks to infer internal state, material condition, or geometry from
sparse resonance data, the same question arises: which aspects of shape are
merely descriptive, and which make the inverse problem possible?  The present
programme suggests that this is the right question to ask first.

If one permits a final compression of the argument into a single sentence, it is
this: the joke was never the point.  Geometry was.  The next tasks are
therefore clear.  The formal results should be tested experimentally in
phantoms and, where feasible, in vivo; the framework should be extended to
nonlinear and more realistic shell models; and the present proofs should be
generalised beyond the reduced axisymmetric class.  Those steps would not
change the direction of the present paper.  They would make it harder to
ignore.
