% =============================================================================
% Section 1: Introduction
% =============================================================================
% PURPOSE:
%   Introduce geometry as the unifying thread across the research programme.
%   Frame the problem: fluid-filled viscoelastic shells appear throughout
%   biomechanics and postharvest science, yet practitioners treat each
%   application in isolation, missing the common geometric structure.
%   State the four-result thesis and outline the paper.
% =============================================================================

\section{Introduction}
\label{sec:introduction}

Spectral questions recur across mathematics, physics, and engineering.  Given
an observed set of resonances, what can one infer about the system that
produced them?  Kac's celebrated formulation --- ``Can one hear the shape of a
drum?'' --- remains the canonical version of this problem~\cite{Kac1966}.  Its
enduring influence lies not in the narrow case of planar drums, but in the
larger programme it inaugurated: to understand which features of a physical
system are encoded in spectral data, which are hidden by symmetry, and which
are unrecoverable without additional information.  The classical counterexample
of isospectral but non-congruent domains~\cite{Gordon1992} did not end that
programme.  It sharpened the question.  Inverse vibration theory, model updating, and
elastographic parameter recovery all ask variations of the same question:
when does a resonance spectrum carry enough independent information to support
reliable inference about geometry, material properties, or both~\cite{Gladwell2004,Gladwell2005,MottersheadFriswell1993,FriswellMottershead1995,Doyley2012}?

In this paper we ask that question for fluid-filled viscoelastic shells.  This
class of systems appears in apparently disparate settings: the human abdomen
and bladder in biomechanics, gas-pocket and sub-bass coupling in physiological
acoustics, and fruit-ripeness assessment in postharvest sensing
~\cite{BrowntoneP1,BrowntoneP2,BrowntoneP4,BrowntoneP6,BrowntoneP7}.  Yet
these applications are linked by one structural fact.  The shell geometry does
not merely set a boundary condition for a forward calculation.  It mediates the
entire problem.  Geometry filters how external forcing couples into admissible
deformation fields; it organises the modal spectrum through curvature,
symmetry, and fluid loading; and it determines whether the resulting spectrum
can be inverted to recover the parameters that generated it.  Our central
thesis is therefore simple: \emph{in fluid-filled viscoelastic shells, geometry
does three jobs --- it filters forcing, organises spectra, and determines
invertibility.}

The first of these roles emerges on the excitation side.  A fluid-filled
oblate shell can possess a genuine low-frequency flexural resonance near
\SI{4}{\hertz}, yet airborne infrasound couples to that mode only weakly
because the long-wavelength forcing field is itself filtered by
geometry~\cite{BrowntoneP1}.  The same shell, driven mechanically through
whole-body vibration, responds far more strongly because that pathway is not
subject to the same spatial-harmonic suppression.  Analyses of sub-\SI{20}{\hertz}
excitation reach the same conclusion: structure-borne pathways dominate
airborne ones in this regime~\cite{BrowntoneP6}.  The point is broader than the
original brown-note motivation.  Resonance cannot be interpreted in isolation
from how forcing projects onto the mode shapes permitted by the geometry.

The second role is spectral organisation.  Fluid-filled shells do not possess a
featureless ladder of frequencies.  Curvature, aspect ratio, internal loading,
and wall compliance sort the admissible motions into qualitatively distinct
families and shift their ordering in application-specific ways
~\cite{Leissa1973,Soedel2004,Junger1986}.  In the abdominal model, this
distinguishes low-frequency flexural modes from the much higher breathing mode
dominated by the compressibility of the entrained fluid~\cite{BrowntoneP1}.  In
the bladder, changing fill volume alters both size and effective stiffness,
producing a non-trivial resonance trajectory rather than simple monotonic
scaling~\cite{BrowntoneP4}.  In borborygmi, constrained gas pockets introduce a
different but related spectral mechanism, in which shell confinement selects the
audible range of bubble oscillations~\cite{BrowntoneP5}.  In watermelon
tap-tone analysis, the measurable spectral shifts used informally by growers are
again organised by geometry and shell mechanics rather than by material changes
alone~\cite{BrowntoneP7}.  Across domains, geometry is the underlying organiser of
what the spectrum is allowed to look like.

The third role is inverse.  A forward model may predict frequencies accurately
enough for classification, explanation, or design, yet still fail as an
inversion model because the spectrum does not separate the parameters cleanly.
That distinction emerged most clearly in the fruit and organ inverse problems
studied in~\cite{BrowntoneP7,BrowntoneP8}.  Equivalent-radius reductions can reproduce leading-order
resonance trends with useful accuracy, which explains their practical appeal.  But
by collapsing shape information into a single scalar radius they confound
geometric and material effects, and the inverse map becomes nearly singular or
formally rank deficient~\cite{BrowntoneP7,BrowntoneP8}.  Recovering
invertibility requires more than a good forward fit.  It requires modal data in
which different modes sample curvature differently.  That requirement is
geometric before it is statistical.

The capstone develops this programme around four formal results --- two
theorems, one proposition, and one lemma --- each of which captures one aspect
of the geometry--spectrum--inversion relation.  The first theorem shows that
equivalent-radius models of non-spherical fluid-filled shells generically
collapse independent geometric information and therefore produce ill-posed
spectral inversion problems.  The second theorem shows that oblate asphericity
can restore invertibility because distinct modes respond differently to
distinct curvature channels.  The proposition establishes the corrected
near-spherical asymptotics: the exact sphere is singular, and the restored
identifiability grows regularly as $\sigma_3(\varepsilon)=\lambda_1
\varepsilon^2+O(\varepsilon^4)$.  The lemma constructs a counterexample showing that a model may be
adequate for predicting resonant frequencies while remaining inadequate for
parameter recovery.  Taken together, these formal results recast several
apparently separate Browntone results as instances of one general statement
about how geometry governs both excitation and inference.

The evidence for that statement accumulated in three stages.  The initial
abdominal and gas-pocket analyses identified the coupling disparity between
airborne and mechanical excitation and established that alternative resonant
substructures can couple far more efficiently than the whole cavity
~\cite{BrowntoneP1,BrowntoneP2}.  A second group of studies broadened the
evidence base: scaling laws indicated that the dimensionless resonance
structure persists across body sizes; bladder resonance revealed
geometry--stiffening competition in another organ; borborygmi provided an
audible constrained-bubble counterpart; and sub-bass coupling extended the
excitation analysis to lower frequencies and alternative pathways
~\cite{BrowntoneP3,BrowntoneP4,BrowntoneP5,BrowntoneP6}.  The inverse studies
then supplied the theoretical turn.  Shell-resonance inversion can succeed when
the geometry leaves enough spectral structure to exploit, whereas asphericity
can lift inverse degeneracy and near-spherical models can remain useful in
forward prediction while unstable in inversion~\cite{BrowntoneP7,BrowntoneP8}.  The present paper treats those
results not as a sequence of case studies, but as evidence for a single
geometry-mediated theory of excitation, resonance, and identifiability.

Our aim is therefore synthetic rather than merely archival.  We do not repeat
the detailed derivations of the companion papers.  Instead, we extract the
shared mathematical structure, prove four formal results in a common language,
and show how the examples together support a general picture of fluid-filled
shells as systems in which symmetry and curvature govern both what can be
excited and what can be inferred.  The intended scope is wider than the original
applications.  The same logic should matter wherever one seeks to infer
geometry or material properties from resonance data in soft shell-like
structures, whether in biomechanics, non-destructive evaluation, or allied
inverse problems.

The paper is organised as follows.  Section~\ref{sec:background} summarises the
programme-level evidence from the companion studies and identifies the common geometric
structure that links them.  Section~\ref{sec:theory} states and proves the
four formal results, together with a supporting proposition for excitation
filtering, and relates them to the underlying shell and inverse problem
theory.  Section~\ref{sec:results} gathers the principal cross-paper results
into a unified comparative account, emphasising where excitation, spectral
organisation, and identifiability align or diverge.  Section
\ref{sec:discussion} considers the broader implications for spectral inference
in fluid-filled shells and for the use of reduced models in inverse settings.
Section~\ref{sec:conclusion} closes with the capstone claim: geometry is not a
secondary detail of these systems, but the mechanism that mediates their
forcing, their resonances, and the possibility of hearing the parameters that
made them.
