% =============================================================================
% Section 3: Theory — Four Conjectures Formalised
% =============================================================================

\section{Theory}
\label{sec:theory}

The companion papers established three ingredients that we now place in a
common mathematical frame.  Paper~1 distinguished the low-frequency flexural
family from the much higher breathing mode in a fluid-filled soft shell, and
showed that geometry controls not only resonance but also the efficiency with
which forcing projects onto those modes~\cite{BrowntoneP1}.  Paper~7 showed that
an equivalent-sphere model can nevertheless be operationally useful when the
inverse task is deliberately narrow and the geometry is known
independently~\cite{BrowntoneP7}.  Paper~8 then exposed the inverse price of that
reduction: once geometry and material must be inferred simultaneously, the same
equivalent-radius simplification becomes structurally defective
~\cite{BrowntoneP8}.  The present section formalises that programme as four
conjectures.

We emphasise at the outset that the statements below concern \emph{local
practical identifiability} of flexural spectra.  They do not claim global
uniqueness for arbitrary nonlinear inversions.  They ask a more disciplined
question: given a nominal operating point, do the measured modal frequencies
contain enough linearly independent information to distinguish changes in
geometry from changes in material stiffness?

\subsection{Common setup}

Consider a fluid-filled viscoelastic shell with semi-major axis $a$,
semi-minor axis $c$, Young's modulus $E$, and fixed secondary parameters
\[
  \mathbf{p}
  =
  (h,\nu,\rho_w,\rho_f,K_f,P_\mathrm{iap},\eta).
\]
For the Browntone applications, the canonical values are
$E=\SI{0.1}{\mega\pascal}$, $a=\SI{0.18}{\metre}$, $c=\SI{0.12}{\metre}$,
$h=\SI{0.01}{\metre}$, $\nu=0.45$,
$\rho_w=\SI{1100}{\kilogram\per\metre\cubed}$,
$\rho_f=\SI{1020}{\kilogram\per\metre\cubed}$,
$K_f=\SI{2.2}{\giga\pascal}$,
$P_\mathrm{iap}=\SI{1000}{\pascal}$, and $\eta=0.25$
~\cite{BrowntoneP1,BrowntoneP8}.  We restrict attention to the flexural modes
$n \geq 2$, since the breathing mode $n=0$ is fluid-compressibility dominated
and lies in the kilohertz range for the canonical abdomen rather than the
single-digit-hertz range of interest~\cite{BrowntoneP1}.  That distinction is
not decorative; it keeps the physics honest.

Let the unknown parameter vector be
\begin{equation}
  \boldsymbol{\theta} = (a,c,E)^\top \in \Theta \subset \mathbb{R}^3_{+},
\end{equation}
and let the measured modal set be $\mathcal{M}=\{n_1,\ldots,n_m\}$, with
$m \geq 3$.  The forward map is
\begin{equation}
  \mathbf{f}(\boldsymbol{\theta})
  =
  \bigl(
    f_{n_1}(\boldsymbol{\theta};\mathbf{p}),
    \ldots,
    f_{n_m}(\boldsymbol{\theta};\mathbf{p})
  \bigr)^\top \in \mathbb{R}^m,
  \label{eq:p10_forward_map}
\end{equation}
where $f_n$ is the natural frequency of flexural mode $n$.  The raw Jacobian is
\begin{equation}
  J_{ij}
  =
  \frac{\partial f_{n_i}}{\partial \theta_j},
  \label{eq:p10_raw_jacobian}
\end{equation}
but because the three parameter directions carry different units, the relevant
local sensitivity operator is the \emph{scaled Jacobian}
\begin{equation}
  J_s[i,j]
  =
  \frac{\partial f_{n_i}}{\partial \theta_j}
  \frac{\theta_j}{f_{n_i}}.
  \label{eq:p10_scaled_jacobian}
\end{equation}
Each entry of $J_s$ is dimensionless and measures fractional frequency change
per fractional parameter change.  Let
\begin{equation}
  \sigma_1 \geq \sigma_2 \geq \sigma_3 \geq 0
  \label{eq:p10_singular_values}
\end{equation}
denote the singular values of $J_s$, and define the local conditioning metric
\begin{equation}
  \kappa(J_s) = \frac{\sigma_1}{\sigma_3}.
  \label{eq:p10_condition_number}
\end{equation}
When $\sigma_3=0$, the inverse problem is locally rank deficient.  When
$\sigma_3>0$ but small, the inverse is formally possible but practically
fragile: small frequency errors may be amplified into large parameter errors.
Thus the smallest singular value identifies the least observable parameter
combination, while $\kappa$ measures how badly the geometry conspires against
the experimentalist.

\subsection{Equivalent-radius reductions and lost geometric dimension}

Equivalent-sphere models replace the two-parameter geometry $(a,c)$ by a single
scalar descriptor, typically the equivalent radius
\begin{equation}
  R_\mathrm{eq} = (a^2c)^{1/3},
  \label{eq:p10_req}
\end{equation}
or, more generally, some smooth scalar reduction $g(a,c)$.  Such reductions can
be entirely sensible for forward estimates of resonance magnitude or scaling,
and indeed they are useful in Papers~1 and~7 for precisely that purpose
~\cite{BrowntoneP1,BrowntoneP7}.  The inverse consequence is less cheerful.

\begin{proposition}[Rank collapse under scalar geometric reduction]
\label{prop:p10_scalar_reduction}
Let a reduced forward model satisfy
\begin{equation}
  f_n(a,c,E;\mathbf{p}) = \phi_n\!\bigl(g(a,c),E;\mathbf{p}\bigr)
  \qquad \text{for all } n \in \mathcal{M},
  \label{eq:p10_scalar_model}
\end{equation}
with $g:\mathbb{R}^2_{+}\to\mathbb{R}_{+}$ a smooth scalar function.  Then the
two geometric columns of the Jacobian are everywhere collinear, so that
\begin{equation}
  \operatorname{rank}
  \left[
    \frac{\partial \mathbf{f}}{\partial a},
    \frac{\partial \mathbf{f}}{\partial c}
  \right]
  \leq 1,
\end{equation}
and consequently
\begin{equation}
  \operatorname{rank}(J) \leq 2,
  \qquad
  \operatorname{rank}(J_s) \leq 2.
  \label{eq:p10_rank_bound}
\end{equation}
\end{proposition}

\noindent\emph{Justification.}
By the chain rule,
\[
  \frac{\partial f_n}{\partial a}
  =
  \frac{\partial \phi_n}{\partial g}\,
  \frac{\partial g}{\partial a},
  \qquad
  \frac{\partial f_n}{\partial c}
  =
  \frac{\partial \phi_n}{\partial g}\,
  \frac{\partial g}{\partial c}.
\]
Hence both geometric columns are scalar multiples of the same mode vector
$\bigl(\partial \phi_{n_i}/\partial g\bigr)_{i=1}^m$.  For the specific choice
$g=R_\mathrm{eq}=(a^2c)^{1/3}$, one obtains
\begin{equation}
  \frac{\partial R_\mathrm{eq}}{\partial a}
  = \frac{2}{3}\frac{R_\mathrm{eq}}{a},
  \qquad
  \frac{\partial R_\mathrm{eq}}{\partial c}
  = \frac{1}{3}\frac{R_\mathrm{eq}}{c},
\end{equation}
and therefore the scaled columns satisfy $J_s[:,a]=2\,J_s[:,c]$ exactly.  One
geometric degree of freedom has been removed before any data are fitted.

\begin{conjecture}[Rank-deficiency of equivalent-radius models]
\label{conj:p10_rank_deficiency}
For any fluid-filled shell model in which the geometry enters the flexural
spectrum only through a scalar reduction $g(a,c)$, the local inverse problem
for $\boldsymbol{\theta}=(a,c,E)$ is structurally rank deficient.  In
particular, the scaled Jacobian with respect to $(a,c,E)$ satisfies
\begin{equation}
  \operatorname{rank}(J_s) \leq 2,
\end{equation}
so that one independent combination of $(a,c)$ is unobservable from the modal
frequencies alone.  Equivalent-radius reductions therefore cannot support
independent recovery of both geometric axes and material stiffness, regardless
of how accurately the frequencies are measured.
\end{conjecture}

The conjecture is stronger than a complaint about poor conditioning.  It states
that the missing information is \emph{structural}: no amount of experimental
precision can recover a geometric direction that the model has collapsed into a
single scalar.  One may still estimate $g(a,c)$ and $E$, but not $a$ and $c$
separately.  Paper~8 exhibited this numerically for the equivalent-sphere
reduction, where the nominal condition number reached
$\kappa \approx 1.37\times 10^{10}$, finite only because the derivatives were
approximated numerically rather than taken symbolically~\cite{BrowntoneP8}.

\subsection{Asphericity as an identifiability-lifting perturbation}

To escape Conjecture~\ref{conj:p10_rank_deficiency}, the model must retain at
least two genuinely independent geometric channels.  For an oblate shell this
occurs through curvature anisotropy.  Writing the eccentricity as
\begin{equation}
  \varepsilon = \sqrt{1 - c^2/a^2},
  \label{eq:p10_eccentricity}
\end{equation}
the spherical limit is $\varepsilon=0$, while $\varepsilon>0$ introduces
distinct meridional and circumferential curvature distributions.  In a Ritz or
perturbation formulation, mode $n$ samples those curvature fields through
mode-specific weighting functions.  Schematically,
\begin{equation}
  f_n(\varepsilon)
  =
  f_n^{(0)} + \alpha_n \varepsilon^2 + \beta_n \varepsilon^4 + \cdots,
  \label{eq:p10_mode_expansion}
\end{equation}
where the coefficients $\alpha_n,\beta_n,\ldots$ depend on the mode number
because different mode shapes concentrate strain energy in different regions of
the shell.  The key point is not the polynomial form by itself, but the
variation of these coefficients with $n$.  Once that happens, the $a$- and
$c$-columns of the Jacobian need no longer remain proportional across modes.

\begin{remark}
The relevant mechanism is \emph{mode-dependent curvature sampling}.  Low-order
and higher-order flexural modes do not interrogate the same parts of an oblate
shell with the same weights, so the spectrum acquires more than one geometric
signature.  Geometry ceases to be a single number and resumes its full-time
occupation.
\end{remark}

\begin{conjecture}[Identifiability lifting by asphericity]
\label{conj:p10_lifting}
For an oblate family of fluid-filled viscoelastic shells with
$\varepsilon>0$, retention of the true spheroidal curvature in the forward model
lifts the equivalent-radius degeneracy.  More precisely, for a generic set of
measured flexural modes $\mathcal{M}$ containing at least three modes, there
exists an open set of oblate operating points on which
\begin{equation}
  \operatorname{rank}(J_s) = 3,
\end{equation}
because different modes weight the meridional curvature field differently and
thus produce non-proportional geometric sensitivity columns.  At the canonical
abdominal operating point studied in Paper~8, this lifting is substantial: the
condition number falls from the equivalent-sphere value
$\kappa \approx 1.37\times 10^{10}$ to the oblate Ritz value
$\kappa = 69.4$~\cite{BrowntoneP8}.
\end{conjecture}

This conjecture does not say that every aspherical shell is automatically
well-conditioned.  It says that oblate asphericity restores the \emph{possibility}
of independent recovery by breaking the exact proportionality imposed by scalar
geometric reduction.  Conditioning then becomes a quantitative matter rather
than an algebraic impossibility.

\subsection{Near-spherical asymptotics and the absence of a true power law}

The next question is how the restored identifiability behaves as the shell
approaches spherical symmetry.  The natural temptation is to seek a singular
power law $\kappa \sim \varepsilon^{-\alpha}$ as $\varepsilon \to 0$.  Paper~8
showed that this intuition is misleading for the oblate Ritz family
~\cite{BrowntoneP8}.  Because the oblate perturbation is reflection-symmetric,
odd powers of $\varepsilon$ are suppressed, and the smallest singular value is
better represented by a regular even expansion than by a singular asymptotic
blow-up.

\begin{conjecture}[Near-spherical conditioning asymptotics]
\label{conj:p10_asymptotics}
For the oblate spheroidal shell family with a curvature-resolving forward model,
the smallest singular value of the scaled Jacobian admits a regular expansion
of the form
\begin{equation}
  \sigma_3(\varepsilon)
  =
  \sigma_0 + \lambda_1 \varepsilon^2 + O(\varepsilon^4),
  \qquad \varepsilon \to 0,
  \label{eq:p10_sigma_asymptotic}
\end{equation}
with $\sigma_0>0$.  Consequently,
\begin{equation}
  \kappa(J_s)
  =
  \frac{\sigma_1(\varepsilon)}{\sigma_0 + \lambda_1 \varepsilon^2 + O(\varepsilon^4)}
\end{equation}
has a finite near-spherical floor rather than a true divergence, so there is no
genuine asymptotic power law in the oblate class.  In the canonical computations
of Paper~8, the directly evaluated near-spherical floor was
$\kappa \approx 269$ at $\varepsilon=0.01$, while an intermediate-range fit over
 $\varepsilon\in[0.15,0.85]$ gave $\sigma_0=0.01113$ and
 $\lambda_1=0.00507$, so that the crossover
 $\varepsilon_c=\sqrt{\sigma_0/\lambda_1}=1.48$ lies outside the physical oblate
 range~\cite{BrowntoneP8}.  By contrast, the prolate family does
not exhibit the same oblate lifting trend: its conditioning remains broadly
flat and poor across the practical eccentricity range.
\end{conjecture}

Two clarifications are essential.  First, the finite floor in
Conjecture~\ref{conj:p10_asymptotics} applies to the \emph{oblate
curvature-resolving} model, not to the equivalent-sphere reduction of
Conjecture~\ref{conj:p10_rank_deficiency}; the latter remains exactly rank
deficient in the analytic limit.  Second, the observed effective power-law fits
over moderate eccentricity windows are descriptive rather than asymptotic.  They
summarise a finite interval; they do not reveal a true singular law at the
sphere.  The mathematics here is gentler than the log--log plot first suggests.

\subsection{Forward adequacy and inverse adequacy are different questions}

Reduced models are often judged by forward error alone.  Let
$\mathbf{f}_\mathrm{red}$ denote a reduced model and
$\mathbf{f}_\mathrm{full}$ a geometry-resolving model.  A natural forward metric
is the relative frequency misfit
\begin{equation}
  \mathcal{E}_\mathrm{fwd}
  =
  \frac{\|\mathbf{f}_\mathrm{red}(\boldsymbol{\theta})
  - \mathbf{f}_\mathrm{full}(\boldsymbol{\theta})\|_2}
  {\|\mathbf{f}_\mathrm{full}(\boldsymbol{\theta})\|_2}.
  \label{eq:p10_forward_error}
\end{equation}
An inverse metric, by contrast, must assess the conditioning of the parameter
recovery map; locally, $\kappa(J_s)$ is the appropriate quantity.  There is no
general theorem forcing small $\mathcal{E}_\mathrm{fwd}$ to imply moderate
$\kappa$.  Indeed, the Browntone sequence provides counterexamples in both
directions.

\begin{conjecture}[Forward adequacy does not imply inverse adequacy]
\label{conj:p10_forward_inverse}
There exist reduced models for fluid-filled viscoelastic shells such that
\begin{equation}
  \mathcal{E}_\mathrm{fwd} \ll 1
\end{equation}
over an experimentally relevant parameter range, while the corresponding inverse
problem for $\boldsymbol{\theta}=(a,c,E)$ is unusable because
\begin{equation}
  \kappa(J_s) \gg 1
  \qquad \text{or} \qquad
  \operatorname{rank}(J_s) < 3.
\end{equation}
Equivalently, a model may predict frequencies accurately enough for screening,
classification, or single-parameter calibration, yet fail catastrophically as a
tool for simultaneous recovery of geometry and material properties.
\end{conjecture}

Paper~7 is the benign case.  There the equivalent-sphere reduction is adequate
because the inverse target is essentially one-dimensional: the geometry is
measured independently, the dominant mode is identified, and the task is to map
that frequency to an effective rind modulus~\cite{BrowntoneP7}.  Forward
adequacy is enough because the geometric uncertainty has already been removed by
other means.  Paper~8 is the hostile case.  There the objective is to recover
$(a,c,E)$ jointly from several modal frequencies, and the equivalent-sphere
model fails precisely because its forward map suppresses one geometric
direction~\cite{BrowntoneP8}.  The same simplification that is serviceable in
Paper~7 is therefore defective in Paper~8.  This is not a contradiction.  It is
the point.

The distinction also complements Paper~1.  There the central lesson was that a
correct resonance frequency does not by itself determine the dominant excitation
pathway, because geometry also filters the forcing field~\cite{BrowntoneP1}.
Here the analogous lesson is that a correct frequency prediction does not by
itself determine inverse usability, because geometry also filters the parameter
directions visible to the data.  In both cases, geometry mediates more than the
location of the peaks.

Taken together, Conjectures~\ref{conj:p10_rank_deficiency}--
\ref{conj:p10_forward_inverse} define the capstone thesis in mathematical form.
Scalar geometric reductions collapse one inverse direction; oblate curvature can
restore it; the restoration is regular rather than singular near the sphere; and
forward success is not a licence for inverse use.  The results section tests
these statements against the cross-paper evidence.
