\section{Conclusions}
\label{sec:conclusion}

We have developed a mechanics-based model for the acoustic `thump test''
used to assess watermelon ripeness.  The model delivers an estimate of
the \emph{effective rind stiffness parameter}; the subsequent inference
from stiffness to biological ripeness requires cultivar-specific
calibration that is beyond the scope of this work.  The principal
findings are:

\begin{enumerate}
  \item The watermelon is modelled as a fluid-filled viscoelastic shell
    using an equivalent-sphere approximation: the oblate geometry is
    captured through $R_{\mathrm{eq}} = (a^2 c)^{1/3}$, and the
    eigenfrequency is derived from classical thin-shell theory for a
    sphere of that radius.  The dominant tap-tone corresponds to the
    $n = 2$ flexural mode, identifiable as the lowest spectral peak
    in the impulse response.

  \item The squared frequency $f_2^2$ is linear in the rind
    elastic modulus $E_{\mathrm{rind}}$ when turgor pressure is
    negligible.  This linearity enables a closed-form inversion
    (Eq.~\ref{eq:inversion}) from a single tap-tone measurement to an
    estimate of the effective rind stiffness.  The condition number of
    this inversion is unity with respect to~$f^2$ and
    approximately~2 with respect to~$f$.

  \item Sobol sensitivity analysis confirms that
    $E_{\mathrm{rind}}$ dominates the frequency response
    ($S_T = 0.54 \pm 0.05$), with fruit size as the second most influential
    parameter.

  \item As a secondary result, the dimensionless group
    $\Pi_{\mathrm{ripe}}$ (Eq.~\ref{eq:Pi_ripe}) collapses different
    cultivar geometries onto a narrow band
    ($\Pi_{\mathrm{ripe}} = 0.062 \pm 0.002$ across four cultivars),
    although its biological validity as a ripeness index across
    cultivars has not been established.

  \item Model predictions are benchmarked against published resonance
    measurements on watermelons \cite{Yamamoto1980} and are consistent
    with frequency--stiffness correlations reported for other fruits
    \cite{DeBelieetal2000, ChenDeBaerdemaeker1993}.  These comparisons
    are consistency checks against literature data, not controlled
    experimental validation.
\end{enumerate}

The equivalent-sphere approximation is adequate for the inversion
application because the goal is to recover~$E_{\mathrm{rind}}$ from
$f_2$ at known geometry; since $a$, $c$, and~$h$ are measured
independently, $R_{\mathrm{eq}}$ is determined and the inversion is
well-posed.  However, the model has zero sensitivity to aspect ratio at
constant~$R_{\mathrm{eq}}$: it cannot distinguish a sphere from an
oblate spheroid of equal volume.  A Ritz variational model with explicit
$\zeta$-dependent basis functions would be needed to capture genuine
curvature effects and could improve accuracy for strongly oblate
cultivars ($\zeta < 0.6$).

Future work will pursue: (i)~experimental validation on instrumented
watermelons with destructive reference measurements to establish the
modulus--ripeness calibration chain; (ii)~extension of the model to
include explicit oblate curvature corrections via a Ritz variational
formulation; (iii)~application to other fruits (cantaloupe, coconut,
pumpkin); and (iv)~development of a smartphone-based measurement tool.
