\section{Conclusions}
\label{sec:conclusion}

The central result of this study is a coupling disparity of approximately
$6.6 \times 10^4$ between mechanical whole-body vibration and airborne
acoustic excitation of the human abdominal cavity.  This single quantity,
derived from first-principles shell theory and energy-consistent reciprocity
analysis, resolves a long-standing empirical asymmetry: occupational
whole-body vibration at \SIrange{4}{8}{\hertz} causes well-documented
gastrointestinal effects, while airborne infrasound at comparable frequencies
and extreme intensities does not.

The disparity has a clean physical origin.  The abdominal cavity possesses
two distinct mode families: a breathing mode ($n = 0$) near
\SI{2500}{\hertz}, governed by the fluid bulk modulus and therefore irrelevant
at infrasonic frequencies; and flexural modes ($n \geq 2$) in the
\SIrange{4}{10}{\hertz} range that match ISO~2631 abdominal transmissibility
data.  Airborne sound at these frequencies has a wavelength exceeding
\SI{49}{\metre}, placing the abdomen deep in the Rayleigh regime
($ka \approx 0.01$).  The $(ka)^n$ geometric penalty, compounded by the
air--tissue impedance mismatch, reduces the effective driving pressure by
four orders of magnitude.  An energy-consistent analysis confirms an
absorption efficiency of $\sim 10^{-14}$: the shell is, for practical
purposes, acoustically transparent.  Reaching the mechanotransduction
threshold via airborne infrasound alone would require approximately
\SI{158}{\decibel}---a level at which structural damage to the middle ear,
blast lung injury, and building collapse would all present more immediate
concerns than any intestinal embarrassment.

Mechanical vibration, transmitted through the skeleton and abdominal wall,
couples directly and produces displacements $10^4$ times larger at
occupational exposure levels.  This disparity is not a subtle biomechanical effect
but a straightforward consequence of long-wavelength acoustics and impedance
physics.  Monte Carlo uncertainty quantification confirms the ratio spans
$10^3$--$10^5$ across physiologically realistic parameter ranges, with
elastic modulus accounting for 86\% of total variance.

The brown note, then, is a half-truth.  The resonance it invokes is genuine;
the mechanism it implies is not.  What popular culture attributes to airborne
sound is, in reality, the province of mechanical vibration---a distinction
that matters considerably for occupational health standards and rather less
for horror film screenwriters.

Future work should validate the boundary condition assumptions through finite
element analysis of anatomically realistic geometries, investigate the role of
bowel gas pockets as localised acoustic transducers, and extend the model into
the nonlinear regime relevant to high-amplitude mechanical excitation.
