\section{Discussion}
\label{sec:discussion}

\subsection{The Coupling Disparity}
\label{sec:disc:disparity}

The central result of this study is the $10^3$--$10^4$ factor separating
mechanical from airborne coupling efficiency
(Tables~\ref{tab:airborne}--\ref{tab:mechanical}).  The physical origin of
this disparity lies in two compounding effects: an impedance mismatch and a
geometric filtering penalty.

First, the air--tissue impedance mismatch is severe.  The specific acoustic
impedance of air is $Z_{\mathrm{air}} = \rho_{\mathrm{air}} c_{\mathrm{air}}
\approx \SI{420}{\pascal\second\per\metre}$, while that of soft tissue is
$Z_{\mathrm{tissue}} \approx \SI{1.6e6}{\pascal\second\per\metre}$, giving
a pressure transmission coefficient $T = 2Z_{\mathrm{air}} /
(Z_{\mathrm{air}} + Z_{\mathrm{tissue}}) \approx 5 \times 10^{-4}$.  At the
body surface, more than \SI{99.9}{\percent} of the incident acoustic energy is
reflected.

Second, even the transmitted pressure must couple to the spatial pattern of
a flexural mode.  In the long-wavelength (Rayleigh) limit, $ka \ll 1$, the
$n$-th order component of the incident plane wave scales as $(ka)^n$
\cite{junger2012sound}.  At \SI{7}{\hertz} with
$R_{\mathrm{eq}} = \SI{0.157}{\metre}$, we obtain
$ka = 2\pi f R / c_{\mathrm{air}} \approx 0.0114$ and therefore
$(ka)^2 \approx 1.3 \times 10^{-4}$ for the $n = 2$ flexural mode
(equation~\ref{eq:peff2}).  Physically, the incident wavelength
($\lambda \approx \SI{49}{\metre}$) is nearly 370 times the body diameter;
the pressure field is almost perfectly uniform over the body surface, and
the quadrupolar ($n = 2$) pressure gradient that could drive an
oblate--prolate deformation is vanishingly small.

The energy budget analysis (\S\ref{sec:coupling}) confirms this picture from
an independent perspective.  The radiation damping ratio in air is
$\zeta_{\mathrm{rad}} \approx 10^{-15}$, whereas the structural damping
ratio is $\zeta_{\mathrm{struct}} = 0.125$, so the absorption efficiency
$\zeta_{\mathrm{rad}} / \zeta_{\mathrm{total}} \sim 10^{-14}$.  The shell
is, for practical purposes, acoustically transparent at infrasonic
frequencies.  By contrast, mechanical vibration transmitted through the
skeleton bypasses both barriers entirely: there is no impedance mismatch
(bone couples directly to the peritoneal wall) and no geometric filtering
(the base-excitation drives the $n = 2$ mode at full amplitude via
equation~\ref{eq:Hrel}).

This disparity resolves an apparent paradox in the literature.  Whole-body
vibration at \SIrange{4}{8}{\hertz} is well documented to cause
gastrointestinal distress---including nausea, abdominal pain, and in
extreme cases, incontinence \cite{griffin1990handbook,mansfield2005human}---whereas
airborne infrasound studies at levels up to \SI{150}{\decibel} report no
comparable effects \cite{Moller2004,Leventhall2007}.  The present modal
analysis shows that both observations are consistent with the \emph{same}
underlying resonance.  The two excitation pathways differ not in the
resonance they address, but in the efficiency with which they address it.

\subsection{Implications for the Brown Note Hypothesis}
\label{sec:disc:brownnote}

The results permit a nuanced evaluation of the so-called ``brown note''
hypothesis.  The hypothesis is \emph{half-correct}: abdominal resonance in the
\SIrange{4}{10}{\hertz} band is physically real, well-supported by the
parametric study (\S\ref{sec:results}), and consistent with ISO~2631
transmissibility data \cite{iso2631,kitazaki1998resonance}.  The flexural
$n = 2$ mode at \SI{4.0}{\hertz} (for $E = \SI{0.1}{\mega\pascal}$, relaxed
musculature) falls squarely within the frequency band where occupational
exposure studies report gastrointestinal symptoms.

Where the hypothesis fails is in the \emph{excitation pathway}.  At
\SI{120}{\decibel} SPL---the threshold of pain and well above any
environmental or entertainment exposure---the predicted airborne wall
displacement is \SI{0.014}{\micro\metre} (Table~\ref{tab:airborne}), roughly
two orders of magnitude below the \SIrange{0.5}{2.0}{\micro\metre} activation
threshold of mechanosensitive PIEZO1/2 ion channels \cite{coste2010piezo1}.
Reaching the \SI{1}{\micro\metre} threshold requires approximately
\SI{158}{\decibel},
a level associated only with explosive blasts and rocket launches.  Even at
this extreme, the displacement remains three
orders of magnitude below what routine whole-body vibration
($a_{\mathrm{rms}} = \SI{0.5}{\metre\per\second\squared}$) produces
(Table~\ref{tab:mechanical}).

This framing is, however, \emph{constructive} rather than merely debunking.
The model provides the first quantitative explanation for \emph{why}
whole-body vibration at \SIrange{4}{8}{\hertz} is so effective at producing
gastrointestinal effects: it excites a bona fide flexural resonance of the
fluid-filled abdominal cavity, producing millimetre-scale tissue
displacements that far exceed mechanotransduction thresholds.  The
epidemiological pattern documented by ISO~2631---peak symptom incidence at
\SIrange{4}{8}{\hertz}, with a strong dependence on acceleration
amplitude---is precisely what a resonance-driven mechanism predicts.

\subsection{Alternative Coupling Pathways}
\label{sec:disc:alternatives}

The whole-cavity resonance model of \S\ref{sec:formulation} treats the
abdominal wall as a homogeneous fluid-filled shell.  In reality, two
additional mechanisms provide alternative pathways for airborne sound to
produce tissue displacement: (i)~compression of intestinal gas pockets, and
(ii)~orifice coupling through the upper gastrointestinal tract.  We consider
each in turn.

\subsubsection{Intestinal gas pocket response}

The human intestine normally contains \SIrange{100}{200}{\milli\litre} of
gas distributed in pockets with effective radii ranging from
\SIrange{1}{10}{\centi\metre}.  Unlike the surrounding tissue, these gas
volumes are compressible, and they respond to incident pressure by
expanding and contracting their bounding walls.

The classical Minnaert frequency of a spherical gas bubble of radius $a$ in
a fluid of density $\rho_f$ is \cite{lamb1882}
\begin{equation}
  f_M = \frac{1}{2\pi a} \sqrt{\frac{3\gamma P_0}{\rho_f}},
\end{equation}
where $\gamma = 1.4$ is the ratio of specific heats and $P_0$ is the
ambient pressure.  For physiological pocket radii of
\SIrange{1}{10}{\centi\metre}, this yields Minnaert frequencies in the range
\SIrange{33}{330}{\hertz}---well above the infrasonic band of interest.  At
\SI{7}{\hertz}, the frequency ratio $f / f_M \approx 0.02$--$0.2$, so gas
pockets are driven far below resonance and experience no resonant
amplification ($H \approx 1.0$).

Nevertheless, in the sub-resonant regime the gas pocket wall displacement
is governed by the quasi-static compliance of the trapped gas:
\begin{equation}
  \xi_{\mathrm{gas}} \approx \frac{p_{\mathrm{inc}} \, a}{3 \gamma P_0},
\end{equation}
which scales linearly with pocket radius and is independent of frequency.
At \SI{120}{\decibel} SPL ($p_{\mathrm{inc}} = \SI{20}{\pascal}$) and
$a = \SI{2}{\centi\metre}$, this yields
$\xi_{\mathrm{gas}} \approx \SI{0.94}{\micro\metre}$---within the PIEZO
activation range and roughly seven times the whole-cavity airborne
displacement of \SI{0.014}{\micro\metre} at the same SPL.  For larger pockets
($a = \SI{5}{\centi\metre}$), the displacement rises to approximately
\SI{2.4}{\micro\metre}, exceeding the threshold with a modest margin.

Crucially, at \SI{7}{\hertz} the acoustic wavelength (\SI{49}{\metre})
vastly exceeds the body diameter, so the pressure field inside the body is
spatially uniform to within $(ka)^2$ corrections.  The gas pockets therefore
experience the full incident pressure, without the geometric filtering
penalty that suppresses whole-cavity flexural excitation.  The mechanism
operates as a local pressure-to-displacement transducer embedded within
the tissue, rather than as a global shell resonance.

This gas pocket pathway has two important implications.  First, it may
explain the well-documented inter-individual variability in infrasound
sensitivity: bowel gas content varies enormously
(\SIrange{50}{500}{\milli\litre}) with diet, gut motility, and
microbiome composition, and individuals with greater gas volume would present
more sites for pressure--displacement conversion.  Second, the mechanism does
not require resonance and operates at any frequency in the sub-wavelength
regime, broadening the range of potentially relevant exposures.

\subsubsection{Orifice coupling through the upper GI~tract}

The mouth and nose provide a low-impedance air pathway to the pharynx
and---when the esophagus is patent---to the stomach.  At \SI{7}{\hertz},
the total path length from mouth to stomach
($L \approx \SI{40}{\centi\metre}$) satisfies $kL \approx 0.05 \ll 1$, so
pressure is transmitted through the air column with negligible
viscothermal attenuation.

With the mouth open and esophagus patent, the pressure reaching the gastric
air bubble is approximately equal to the incident pressure, representing a
transmission ratio of order unity compared with the $(ka)^2 \approx 1.3
\times 10^{-4}$ penalty for body-surface coupling---an enhancement factor
of roughly $7{,}700\times$.  Compression of the gastric gas bubble then
produces wall displacements by the same mechanism described above for
intestinal pockets.

However, this pathway is severely limited by anatomy.  The esophagus is a
collapsible muscular tube that is closed at rest; it opens only during
swallowing (approximately \SIrange{0.5}{1.0}{\second} per event), belching,
or pathological gastroesophageal reflux.  At rest with the mouth open, the
air column terminates at the upper esophageal sphincter, and pressure reaches
only the supraglottic space.  The orifice pathway is therefore
\emph{intermittent}, dependent on the state of the upper GI sphincters, and
cannot be relied upon as a continuous coupling mechanism.

\subsubsection{Assessment of alternative pathways}

Table~\ref{tab:pathway_summary} summarises the predicted displacement for
each coupling mechanism at \SI{120}{\decibel} SPL and \SI{7}{\hertz}.
\begin{table}[htbp]
  \centering
  \caption{Comparison of coupling mechanisms at \SI{120}{\decibel} SPL,
  \SI{7}{\hertz}.}
  \label{tab:pathway_summary}
  \begin{tabular}{lcc}
    \hline
    Mechanism & $\xi$ ($\mu$m) & PIEZO? \\
    \hline
    Cavity resonance ($n{=}2$, airborne) & 0.014 & No \\
    Gas pocket $a = \SI{2}{\centi\metre}$ (airborne) & 0.94 & Marginal \\
    Gas pocket $a = \SI{5}{\centi\metre}$ (airborne) & 2.4 & Yes \\
    Orifice (open mouth $\to$ stomach) & $\sim$0.5 & Marginal \\
    WBV at \SI{0.5}{\metre\per\second\squared} (mech.) & 4{,}586 & Yes \\
    WBV at \SI{1.15}{\metre\per\second\squared} (mech.) & 10{,}549 & Yes \\
    \hline
  \end{tabular}
\end{table}

Even with the most favourable alternative pathway (a large,
\SI{5}{\centi\metre}-radius gas pocket at \SI{120}{\decibel}), the airborne
displacement remains two to three orders of magnitude below what mechanical
coupling achieves at the EU Whole-Body Vibration Directive action value of
\SI{0.5}{\metre\per\second\squared}.  The alternative pathways therefore do
not alter the principal conclusion of this work---that airborne infrasound is
an ineffective excitation route compared with mechanical vibration---but they
provide a physically grounded explanation for why rare, sporadic
gastrointestinal responses to extreme infrasound (\SI{>120}{\decibel}) are
not entirely implausible, and why such responses exhibit large
inter-individual variability.

\subsection{Clinical and Occupational Relevance}
\label{sec:disc:clinical}

The coupling disparity has direct implications for occupational exposure
standards.  ISO~2631-1 specifies frequency-weighted acceleration limits for
whole-body vibration, with the highest sensitivity weighting in the
\SIrange{4}{8}{\hertz} band---precisely the range where our model predicts
the $n = 2$ flexural resonance \cite{iso2631}.  The EU Physical Agents
(Vibration) Directive~2002/44/EC codifies two thresholds: a daily exposure
action value of \SI{0.5}{\metre\per\second\squared} $A(8)$ and an exposure
limit value of \SI{1.15}{\metre\per\second\squared} $A(8)$.  At the action
value, our model predicts a relative abdominal wall displacement of
\SI{4.6}{\milli\metre} at resonance (Table~\ref{tab:mechanical})---more than
$4{,}000\times$ the PIEZO activation threshold.  The present analysis
therefore provides a \emph{mechanistic rationale} for why these particular
frequency bands and amplitude thresholds were empirically selected: they
correspond to conditions under which flexural resonance of the abdominal
cavity produces tissue strains large enough to activate
mechanotransduction pathways.

For airborne infrasound, ISO~7196 defines G-weighting but prescribes no
dose--response limits.  Our analysis supports this regulatory asymmetry:
at environmental and occupational SPL ($\leq \SI{120}{\decibel}$), airborne
coupling to abdominal flexural modes is negligible, and exposure limits
based on abdominal resonance effects are unnecessary at these levels.

A potentially valuable extension of this framework is toward personalised
vibration exposure assessment.  The parametric study (\S\ref{sec:results})
shows that the $n = 2$ eigenfrequency depends sensitively on body habitus:
larger abdominal radius (higher BMI) reduces the resonance frequency, while
greater muscular tone (higher effective $E$) increases it.  In principle,
imaging-derived geometric parameters \cite{parker2011imaging} combined with
the analytical expressions of \S\ref{sec:formulation} could yield
subject-specific resonance frequency estimates, enabling targeted vibration
exposure limits for workers whose body habitus places their resonance
frequency in a particularly hazardous band.

\subsection{Nonlinear Amplitude Effects}
\label{sec:disc:nonlinear}

The linear model of \S\ref{sec:formulation} is valid only for small
displacements.  To bound the error at occupational vibration amplitudes, we
performed a Duffing-type perturbation analysis incorporating membrane
stretching and fluid volume conservation, yielding a hardening nonlinearity
coefficient $\alpha = 7.07 \times 10^7$.

The onset of appreciable nonlinearity (\SI{5}{\percent} frequency shift) occurs
at a wall displacement of \SI{1091}{\micro\metre} ($A/h = 0.109$).  At the EU
action value of \SI{0.5}{\metre\per\second\squared}, the linear model predicts
a peak displacement of \SI{4586}{\micro\metre}; the nonlinear correction
reduces this to \SI{2258}{\micro\metre}, a \SI{51}{\percent} reduction.  The
forcing exceeds the jump-phenomenon threshold ($\SI{0.5}{\metre\per\second
\squared} > \SI{0.12}{\metre\per\second\squared}$), so the actual response
curve exhibits hysteresis and amplitude-dependent frequency shifts.  All modes
$n = 2$--$6$ cross the nonlinearity threshold within the predicted whole-body
vibration range.

Crucially, the hardening behaviour means that the linear model
\emph{overestimates} peak displacement under mechanical excitation.  For the
brown note argument, this is a conservative error: the true mechanical coupling
is somewhat weaker than the linear prediction, while the airborne displacement
($\sim\SI{0.014}{\micro\metre}$) remains deep in the linear regime.  The
$10^3$--$10^4$ coupling disparity therefore represents an upper bound; the true
ratio is, if anything, smaller but still overwhelming.

\subsection{Limitations}
\label{sec:disc:limitations}

We identify the following limitations, grouped by their likely effect on
the conclusions.

\begin{enumerate}

  \item \textbf{Linear theory.}  The Love--Kirchhoff shell formulation
    assumes small displacements.  The nonlinear analysis of
    \S\ref{sec:disc:nonlinear} shows that occupational vibration amplitudes
    exceed the \SI{5}{\percent} nonlinearity threshold ($A/h > 0.109$), with
    the hardening response reducing peak displacement by up to
    \SI{51}{\percent} relative to the linear prediction.  Because the airborne
    displacement remains deep in the linear regime, this nonlinearity
    \emph{reduces} the coupling ratio somewhat but does not alter the
    qualitative conclusion.

  \item \textbf{Homogeneous, isotropic wall.}  The abdominal wall is a
    layered anisotropic composite comprising four muscle layers, fascia,
    subcutaneous fat, and skin.  Our laminate analysis (not reproduced here)
    shows that homogenisation introduces less than \SI{5}{\percent} error in
    the effective bending stiffness.  The isotropic assumption is a
    first-order approximation; anisotropy would split the mode degeneracies
    of the equivalent sphere but would not change the order of magnitude of
    the eigenfrequencies or the coupling ratio.

  \item \textbf{Free-shell boundary conditions.}  The abdomen is partially
    constrained by the spine posteriorly, the pelvis inferiorly, and the
    rib cage superiorly.  The Rayleigh--Ritz boundary condition study
    (\S\ref{sec:bc_effects}) shows that even clamping \SI{25}{\percent} of
    the shell surface shifts $f_2$ by only \SI{11.4}{\percent}, because the
    fluid added mass ($7.4\times$ the shell mass for $n=2$) dominates the
    system inertia.  This shift is well within the material property
    uncertainty band, validating the free-shell approximation.  The coupling
    ratio is unaffected because both excitation pathways address the same
    modal structure.

  \item \textbf{Thin-shell approximation.}  The wall-thickness-to-radius
    ratio ($h/R \approx 0.06$) lies near the conventional upper bound of
    thin-shell theory ($h/R < 0.05$).  First-order shear-deformation
    (Mindlin--Reissner) corrections would reduce the $n = 2$ frequency by
    approximately \SI{4}{\percent} \cite{Soedel2004}, a negligible effect
    compared with the material-property uncertainty.  This limitation is
    unlikely to affect any conclusions.

  \item \textbf{Equivalent-sphere geometry.}  The oblate spheroidal
    abdomen is mapped to an equivalent sphere via $R_{\mathrm{eq}} =
    (a^2 c)^{1/3}$.  This preserves volume and leading-order curvature
    but suppresses the equatorial--polar mode splitting that occurs in
    an oblate spheroid \cite{Leissa1973}.  For a typical aspect ratio
    $c/a = 0.67$, the splitting is estimated at ${\sim}\SI{33}{\percent}$,
    which could shift individual mode frequencies but would not change the
    coupling ratio or the qualitative separation between breathing and
    flexural mode families.

  \item \textbf{Inviscid fluid assumption.}  The enclosed fluid is modelled
    as inviscid.  A viscous correction using the Stokes boundary-layer
    thickness shows that even at the worst-case mucus viscosity
    ($\mu = \SI{0.1}{\pascal\second}$), the quality factor decreases by only
    $\Delta Q = -1.85\%$.  The crossover viscosity at which viscous damping
    would equal structural damping is \SI{281}{\pascal\second}---the
    consistency of peanut butter.  The inviscid assumption is therefore
    well justified for any physiologically realistic abdominal fluid.

  \item \textbf{No internal organ structure.}  Visceral organs are
    homogenised into a single fluid.  An effective-medium analysis with
    solid inclusions (liver, spleen, kidneys) at a volume fraction
    $\phi = 0.25$ predicts a frequency shift of only \SI{0.4}{\percent} for
    the $n=2$ mode.  The organ tissue bulk modulus
    ($K_\mathrm{tissue} \approx K_\mathrm{water}$) produces zero effective
    bulk modulus change, and at sub-percolation volume fractions the isolated
    inclusions cannot transmit shear.  The homogeneous fluid model is
    therefore adequate for the present purposes.

  \item \textbf{Gas pocket model simplifications.}  The gas pocket analysis
    (\S\ref{sec:disc:alternatives}) treats intestinal gas as spherical
    bubbles in an infinite homogeneous fluid, neglecting the cylindrical
    geometry of the gut lumen, viscoelastic wall loading, and the
    surrounding organ structure.  These simplifications likely
    \emph{overestimate} gas pocket displacement, because intestinal wall
    mass loading and stiffness would reduce the effective compliance.  A
    coupled gas--tissue finite-element model is needed to refine these
    estimates.

  \item \textbf{Mechanotransduction thresholds.}  The
    \SIrange{0.5}{2.0}{\micro\metre} PIEZO activation range
    \cite{coste2010piezo1} derives from cell-culture experiments and may
    not directly translate to tissue-scale effects, where strain
    concentrations around cells are modulated by the extracellular matrix.
    This limitation introduces uncertainty in the absolute threshold but
    does not affect the \emph{relative} comparison between airborne and
    mechanical coupling.

\end{enumerate}

\noindent
In summary, the identified limitations affect the absolute values of
predicted frequencies and displacements---in several cases substantially---but
none alter the central finding that airborne acoustic coupling to abdominal
flexural modes is $10^3$--$10^4$ times weaker than mechanical coupling under
occupationally relevant conditions.

\subsection{Proposed Experimental Validation}
\label{sec:disc:validation}

We propose a two-stage experimental programme to validate the key
predictions of the analytical model.  The first stage employs a
tissue-mimicking phantom: an oblate spheroidal silicone shell
($a = \SI{0.18}{\metre}$, $c = \SI{0.12}{\metre}$, $h = \SI{10}{\milli\metre}$)
filled with degassed water, matching the canonical geometry of
\S\ref{sec:formulation}.  The shell material is platinum-cure silicone
(Ecoflex~00-30 to Dragon~Skin~10A), whose Young's modulus spans
\SIrange{0.07}{0.15}{\mega\pascal}---bracketing the relaxed abdominal wall
estimate of $E = \SI{0.1}{\mega\pascal}$.  By casting phantoms at several
mixing ratios, the $f_2 \propto \sqrt{E}$ dependence can be tested
directly.  Modal frequencies are measurable with an instrumented impact
hammer or a low-frequency shaker sweep, and mode shapes can be
reconstructed with a scanning laser vibrometer (Polytec PSV-500).
The predicted $n = 2$ frequency for the recommended Ecoflex~00-30
formulation is \SI{2.5}{\hertz}; for Dragon~Skin~10A,
\SI{3.6}{\hertz}; the model predicts \SI{4.0}{\hertz} for the
canonical human case.

The critical measurement is the coupling-ratio comparison.  By mounting
the phantom on an electrodynamic shaker (mechanical pathway) and
separately exposing it to a subwoofer-generated infrasound field at
\SI{120}{\decibel} (airborne pathway), the displacement ratio
$\xi_{\mathrm{mech}} / \xi_{\mathrm{air}}$ can be measured in a single
experimental session.  The model predicts ratios of order $10^3$--$10^4$
across the silicone formulation range (Table~\ref{tab:pathway_summary}).
Non-detection of the airborne response at the vibrometer noise floor
($\sim\SI{0.01}{\micro\metre}$) would itself constitute a positive
validation of the weak-coupling prediction.  The total cost of consumables
(silicone, molds, sensors) is estimated at less than US\$\,3\,100, assuming
access to shared laboratory equipment (shaker, laser vibrometer, DAQ).

The second stage extends to in~vivo human subjects.  Subject-specific
abdominal wall moduli would be obtained via magnetic resonance elastography
or shear-wave ultrasound elastography, and whole-body vibration
transmissibility measured on an ISO~2631-compliant platform at sub-action-value
amplitudes (\SI{0.3}{\metre\per\second\squared}).  A sample of 15 subjects,
spanning a range of body habitus, is sufficient (power $= 0.80$,
$\alpha = 0.05$) to detect a paired-test effect size $d = 1.0$ between
measured and predicted peak-transmissibility frequencies.  This programme
requires Institutional Review Board approval and is estimated at
8--12~months, with the phantom study serving as a prerequisite validation of
the model physics under controlled conditions.
