\section{Introduction}
\label{sec:introduction}

Whole-body vibration in the \SIrange{4}{8}{\hertz} range causes
gastrointestinal disturbances.  This is not folklore---it is an occupational
health fact, codified in ISO~2631~\cite{iso2631}, reviewed by
Griffin~\cite{griffin1990handbook} and Mansfield~\cite{mansfield2005human},
and documented among truck drivers, helicopter pilots, and heavy-equipment
operators worldwide.  Airborne sound at the same frequencies does not produce
these effects, even at extreme intensities.  NASA-funded exposures at
140--154\,dB\,SPL caused chest-wall vibration and respiratory disruption, but
\emph{no gastrointestinal response whatsoever}~\cite{Mohr1965}.  Two
excitation pathways, the same target organ, the same frequency band---yet
outcomes that differ by orders of magnitude.  Why?

The question has a popular-culture shadow.  The ``brown note''---a
hypothetical infrasonic tone said to cause involuntary bowel movements---has
circulated in military folklore, audio engineering lore, and popular media for
decades, surviving at least one televised debunking~\cite{Leventhall2007}.
As a scientific hypothesis, it has been dismissed but never properly
\emph{examined}; as a cultural phenomenon, it neatly encapsulates the public
confusion between what mechanical vibration demonstrably does and what
airborne sound is assumed to do.  We take the underlying physics
seriously---perhaps more seriously than the subject matter
deserves---while treating the myth as what it is: a vivid misattribution
of mechanism.

The empirical asymmetry between mechanical and airborne excitation is, in
fact, a straightforward consequence of long-wavelength acoustics.  At
the $n{=}2$ resonance ($f_2 \approx \SI{4}{\hertz}$) the acoustic wavelength
exceeds \SI{85}{\metre}---more than 250 times the abdominal diameter.  In
this deep Rayleigh regime, the $n$-th spatial harmonic of the incident field
scales as $(ka)^n$, where $ka \approx 0.01$.  Flexural deformation of the
abdominal wall ($n \geq 2$) therefore receives a driving pressure four orders
of magnitude below the free-field value.  Compound this geometric penalty with the air--tissue
impedance mismatch, and the coupling deficit becomes enormous.  Mechanical
vibration, transmitted through the skeleton and abdominal wall, suffers
neither penalty.  The ratio between these two pathways---the \emph{coupling
disparity}---is the central quantity we derive and the principal contribution
of this paper.

The physics has a longer pedigree than the \emph{South Park} episode that
popularised the brown note.  Gavreau's experiments at CNRS Levallois-Perret
in the late 1950s, where a faulty ventilator at approximately
\SI{7}{\hertz} caused nausea among laboratory
staff~\cite{Gavreau1966,Leventhall2007},
drew early attention to infrasound.  Von~Gierke's systematic review for
NASA~\cite{vonGierke1974,vonGierke2002} established exposure criteria that
informed later ISO standards.  Tandy and Lawrence~\cite{Tandy1998}
demonstrated that a \SI{19}{\hertz} standing wave could induce visual
disturbances and anxiety---real perceptual effects, but far from the claimed
bowel response.  Critical reviews by
Leventhall~\cite{Leventhall2003,Leventhall2007} and assessments of acoustic
weapons by Altmann~\cite{Altmann1999} and Jauchem and
Cook~\cite{Jauchem2007} concluded that infrasound is impractical as a weapon
and that claims of extreme physiological effects are exaggerated or
fabricated.  Yet none of this work quantified \emph{why} airborne and
mechanical pathways differ so dramatically---the conclusion was empirical,
not mechanistic.

We provide the mechanistic account.  No prior study has:
\begin{enumerate}
  \item derived abdominal cavity eigenfrequencies from first-principles
    shell theory with proper fluid--structure coupling;
  \item quantified the airborne acoustic coupling coefficient for flexural
    modes in the long-wavelength limit; or
  \item compared airborne and mechanical excitation pathways within a common
    energy-budget framework to obtain a single, quantitative coupling ratio.
\end{enumerate}

We address all three gaps.  We model the abdomen as a fluid-filled
viscoelastic oblate spheroidal shell, derive natural frequencies for both
breathing ($n=0$) and flexural ($n \geq 2$) mode families, and compare
airborne acoustic coupling---subject to a severe $(ka)^n$ penalty at
infrasonic wavelengths---against direct mechanical (whole-body) vibration
coupling, which suffers no such penalty.

The result is a coupling disparity of approximately $6.6 \times 10^4$ between
mechanical and airborne pathways.  This single number---robust across
physiologically realistic parameter ranges, as we confirm through Monte Carlo
uncertainty quantification---resolves the empirical asymmetry cleanly.  It
explains why whole-body vibration at \SIrange{4}{8}{\hertz} produces
well-documented gastrointestinal effects, why airborne infrasound at
comparable frequencies does not, and why the brown note belongs to acoustics
folklore rather than acoustics fact.

The remainder of this paper is organised as follows.
Section~\ref{sec:formulation} develops the mathematical formulation.
Section~\ref{sec:results} presents a parametric study and validates the model
against ISO~2631 data.  Section~\ref{sec:coupling} quantifies the coupling
disparity.  Section~\ref{sec:discussion} discusses implications, alternative
pathways, and limitations, and Section~\ref{sec:conclusion} draws conclusions.
