\section{Conclusions}
\label{sec:conclusion}

We have modelled the human urinary bladder as a fluid-filled viscoelastic
spherical shell and computed its flexural mode frequencies across the
physiological fill range.  The principal findings are:

\begin{enumerate}
  \item The fundamental flexural mode ($n = 2$) follows a U-shaped
    frequency--volume curve, with a minimum of \SI{13.5}{\hertz} at
    \SI{222}{\milli\litre}, arising from the competition between geometric
    softening (increasing radius and thinning wall) and strain-stiffening of
    the detrusor muscle.  For fill volumes of
    \SIrange{150}{500}{\milli\litre} where the thin-shell assumption is
    valid ($h/R < 0.1$), $f_2$ spans \SIrange{13.5}{17.1}{\hertz}.
    This non-monotonic, fill-dependent resonance behaviour is the central
    physical contribution of this work.

  \item The sub-resonant forced response is the practically dominant
    excitation mechanism under occupational WBV.  At \SI{6}{\hertz}
    (near the pelvic transmissibility peak), the predicted wall displacement
    ($\sim$\SI{160}{\micro\metre}) exceeds the at-resonance displacement
    ($\sim$\SI{47}{\micro\metre}) by a factor of 3--4$\times$, because the
    larger seat displacement amplitude and pelvic amplification more than
    compensate for the reduced bladder modal response.

  \item Mechanical vibration transmitted through the pelvic skeleton is
    approximately $6{,}400$ times more effective than airborne sound at
    exciting the bladder's $n = 2$ mode at \SI{300}{\milli\litre} fill.
    This coupling disparity, driven by the $(ka)^2$ penalty in the Rayleigh
    regime ($ka \approx 0.01$), confirms that whole-body vibration is the
    dominant excitation pathway.

  \item The breathing mode ($f_0 \approx \SI{9500}{\hertz}$) is dominated by
    the fluid bulk modulus and is irrelevant to WBV or infrasonic exposure,
    confirming the same qualitative separation between breathing and flexural
    mode families observed in the larger abdominal cavity.
\end{enumerate}

The model provides a first-principles physical characterisation of
fill-dependent bladder resonance.  Under representative occupational WBV
exposure ($a = \SI{0.5}{\metre\per\second\squared}$), the predicted peak
bladder wall displacements are small relative to physiological deformations
but are delivered at cyclic strain rates ($\sim$\SI{0.1}{\per\second}) that
are approximately 500 times faster than quasi-static filling.  Whether these
strain rates are sufficient to activate bladder mechanotransduction pathways
(particularly the rate-sensitive PIEZO2 channel) remains an open question
requiring experimental investigation.  Future work should characterise the
dynamic activation thresholds of bladder mechanoreceptors at infrasonic
frequencies, incorporate the pelvic boundary constraint through finite
element analysis with anatomically realistic geometry, and pursue
experimental validation of the predicted fill-dependent resonance range.
