\section{Discussion}
\label{sec:discussion}

\subsection{Clinical Implications}
\label{sec:clinical}

The predicted $n = 2$ frequency range (\SIrange{14}{17}{\hertz}) has
immediate relevance to occupational health.  Vehicle cabins expose operators
to broadband vibration spanning \SIrange{1}{20}{\hertz}, with dominant energy
typically concentrated below \SI{10}{\hertz} from engine and road
excitation~\cite{griffin1990handbook,mansfield2005human}.  The bladder's
fundamental mode sits at the upper edge of this band.  Two coupling mechanisms
are therefore relevant:

\paragraph{Sub-resonant forced response.}
At the ISO~2631 pelvic resonance peak (\SIrange{4}{8}{\hertz}), the bladder
responds as a forced sub-resonant oscillator.  The pelvic transmissibility is
at its maximum ($T \approx 2.3$ at \SI{5.5}{\hertz}), and while the bladder
modal amplification is below unity at these frequencies, the product
$T \times H$ remains significant.  This is the regime most relevant to
occupational WBV exposure: the bladder wall undergoes forced cyclic
deformation driven by amplified pelvic motion, even though the excitation
frequency is below the bladder's own resonance.

\paragraph{Near-resonant amplification.}
At the bladder's natural frequency (\SIrange{14}{17}{\hertz}), the modal
amplification reaches its peak ($Q = 2.5$), but pelvic transmissibility has
rolled off ($T \approx 0.3$).  This regime may be relevant to certain
industrial vibration sources (e.g., pneumatic tools, vibratory compactors)
that produce significant energy above \SI{10}{\hertz}.  The
fill-volume-dependent nature of the resonance means that the bladder's
susceptibility to a particular frequency shifts as it fills---a dynamic
vulnerability window.

\paragraph{Displacement quantification.}
To place the model predictions in physiological context, we estimate the
bladder wall displacement under representative occupational WBV exposure.
At the ISO~2631 daily exposure action value
($a_\mathrm{seat} = \SI{0.5}{\metre\per\second\squared}$ RMS), the seat
displacement amplitude at the bladder resonance frequency
($f_2 = \SI{13.4}{\hertz}$ at \SI{300}{\milli\litre}) is
$y_\mathrm{seat} = a/(2\pi f)^2 \approx \SI{70}{\micro\metre}$.  Through
the pelvic skeleton ($T \approx 0.31$), this delivers
$y_\mathrm{pelvis} \approx \SI{22}{\micro\metre}$ to the bladder base.
At resonance, the bladder wall amplifies this by $Q = 2.5$, giving a peak
relative wall displacement of approximately \SI{55}{\micro\metre}---a cyclic
wall strain of $\varepsilon \approx 1.3 \times 10^{-3}$ ($0.13\%$).

In the sub-resonant regime at \SI{6}{\hertz} (near the pelvic
transmissibility peak), the seat displacement is much larger
($\sim$\SI{350}{\micro\metre}) and pelvic amplification is near its maximum
($T \approx 2.0$).  Despite the bladder being below resonance, the relative
wall displacement reaches approximately \SI{170}{\micro\metre}
($\varepsilon \approx 0.4\%$), because the large base displacement more
than compensates for the reduced modal amplification.

\paragraph{Physiological context.}
These vibration-induced displacements are minute compared to the quasi-static
deformations the bladder routinely accommodates.  Normal filling from
\SI{50}{\milli\litre} to \SI{300}{\milli\litre} stretches the wall by
approximately \SI{19}{\milli\metre} ($\varepsilon \approx 81\%$), and
detrusor contraction during micturition---which generates pressures of
\SIrange{40}{60}{cmH_2O}---produces wall displacements of order
\SI{30}{\milli\metre}~\cite{Griffiths1980}.  The WBV displacement of
\SI{55}{\micro\metre} is therefore five orders of magnitude smaller than
the filling displacement and far below the amplitude of normal physiological
wall deformation.

The equivalent quasi-static intravesical pressure perturbation from the
resonant wall strain is only $\Delta p \approx E\varepsilon \approx
\SI{70}{\pascal}$ ($\sim$\SI{0.7}{cmH_2O}), well below the
\SIrange{5}{15}{cmH_2O} threshold at which myelinated A$\delta$ afferents
begin firing in response to slow bladder
distension~\cite{Habler1993,Fowler2008}.  On the basis of static
displacement alone, WBV-induced wall motion would appear physiologically
insignificant.

\paragraph{Dynamic strain rate and mechanotransduction.}
The critical distinction, however, is that WBV delivers its displacement
cyclically at \SIrange{6}{17}{\hertz}, producing peak strain rates of
$\dot{\varepsilon} \approx \SI{0.1}{\per\second}$ at resonance.  This
is approximately 500 times faster than the strain rate during normal filling
($\dot{\varepsilon}_\mathrm{fill} \sim 2 \times 10^{-4}\;\mathrm{s}^{-1}$
for a typical one-hour fill cycle).  Mechanosensitive ion channels in
biological membranes are sensitive to the \emph{rate} of membrane
deformation, not merely its magnitude~\cite{coste2010piezo1}.

Recent work has identified PIEZO2 as the principal low-threshold stretch
sensor in the bladder urothelium and sensory
neurons~\cite{Marshall2020}.  PIEZO2 mediates the earliest sensation of
bladder filling and is essential for normal micturition reflexes; loss of
PIEZO2 function produces impaired bladder-filling sensation and voiding
dysfunction in both mice and
humans~\cite{Marshall2020,Dalghi2021}.  Crucially, PIEZO channels
are tuned to rapid membrane deformation---they inactivate under sustained
stretch but respond robustly to dynamic, cyclic
stimuli~\cite{coste2010piezo1}.  The cyclic strain delivered by WBV, though
small in absolute magnitude, is precisely the class of stimulus to which
these channels are optimised.

Whether the WBV-induced strain rate of $\sim$\SI{0.1}{\per\second} exceeds
the PIEZO2 activation threshold in vivo remains an open question: the
dynamic thresholds of bladder mechanoreceptors have not been characterised
at infrasonic frequencies.  The unmyelinated C-fibre population in the
detrusor, which is normally quiescent (`silent') during physiological
filling but can be recruited by pathological
stimuli~\cite{Fowler2008,Habler1993}, represents an additional potential
pathway for vibration-induced urgency sensitisation.

\paragraph{Clinical scenarios.}
The model provides a first-principles framework for three well-documented
but mechanistically unexplained clinical observations:
\begin{enumerate}
  \item \textbf{Urgency in vehicle occupants.}  Professional drivers exposed
    to broadband WBV at \SIrange{4}{16}{\hertz} report increased urinary
    urgency and frequency~\cite{Seidel1986}.  The model suggests that even
    at the ISO~2631 action level, cyclic bladder wall deformation of
    \SIrange{50}{170}{\micro\metre} occurs across the relevant frequency
    band.  The fill-dependent frequency minimum (\SI{12}{\hertz} near
    \SI{170}{\milli\litre}) means the bladder becomes maximally susceptible
    precisely as it begins to fill---the ``early urge'' fill state.
  \item \textbf{Stress incontinence aggravation.}  Women with pre-existing
    pelvic floor weakness may experience symptom aggravation during vibration
    exposure.  The model predicts that a weakened pelvic floor (lower
    $\zeta_\mathrm{pelvis}$, higher $T$) would deliver larger displacements
    to the bladder wall, potentially amplifying the urgency signal.
  \item \textbf{The ``long drive'' phenomenon.}  The common experience of
    urgency during prolonged vehicle travel---often attributed to cold
    exposure or psychological factors---may have a biomechanical
    contribution: hours of sustained sub-threshold cyclic loading could
    sensitise mechanoreceptor pathways through temporal summation, lowering
    the effective urgency threshold progressively over the journey.
\end{enumerate}


\subsection{Comparison with Other Pelvic Organs}
\label{sec:pelvic}

The bladder is not the only pelvic organ exposed to WBV.  The prostate,
uterus, and rectum are all fluid-containing or fluid-adjacent structures
embedded in the pelvic floor.  The present framework could, in principle,
be adapted to any of these organs by substituting appropriate geometric
and material parameters.  The bladder is simply the cleanest example: a
single-chamber, fluid-filled, roughly spherical shell with well-characterised
mechanical properties.


\subsection{Therapeutic Whole-Body Vibration}
\label{sec:therapeutic}

WBV at \SIrange{20}{40}{\hertz} is increasingly used for pelvic floor
rehabilitation in post-prostatectomy and postpartum
patients~\cite{Pelvic2019}.  The bio\-electrical activity of pelvic floor
muscles increases during synchronous WBV~\cite{Lauper2009}, and clinical
trials report improvements in continence
symptoms~\cite{NCT03325660}.  Our model suggests that these therapeutic
frequencies (\SIrange{20}{40}{\hertz}) lie above the bladder's $n = 2$ mode
for most fill states, placing the bladder in a supra-resonant regime where
wall displacement decreases with frequency.  The therapeutic effect is
therefore more likely mediated by pelvic floor muscle activation than by
direct bladder wall resonance.


\subsection{Limitations}
\label{sec:limitations}

Several simplifications warrant discussion.

\paragraph{Spherical geometry.}
The real bladder is slightly oblate and irregularly shaped, particularly at
low fill states.  A more realistic geometry would modify the mode shapes and
could split the degenerate frequencies of the spherical model.  However, at
moderate-to-high fill the spherical approximation is reasonable, and the
errors are of order $(1 - c/a)^2$ for the eigenfrequencies.

\paragraph{Pelvic constraint.}
Approximately 40\% of the bladder surface is in direct contact with the
pelvic bone and pelvic floor musculature, which constrains the wall motion
over a substantial fraction of the shell.  By Rayleigh's theorem, imposing a
partial rigid boundary on a vibrating structure raises its natural
frequencies: the constraint eliminates admissible trial functions from the
variational space, thereby increasing the Rayleigh quotient.  The free-shell
model therefore provides a \emph{lower} bound on the resonant frequencies.

We can estimate the magnitude of this effect.  If the constraint immobilises
40\% of the shell surface, the effective vibrating mass is reduced (the
constrained region no longer participates in modal displacement) while the
effective stiffness increases (the remaining free surface must accommodate
the same mode shape with a shorter arc length, increasing curvature
gradients).  For the $n = 2$ mode, these combined effects would raise the
natural frequency by an estimated 15--25\%, shifting the predicted range from
\SIrange{14}{17}{\hertz} to approximately \SIrange{16}{21}{\hertz}.  The mode
shapes would also be modified: instead of the symmetric quadrupolar
deformation of a free sphere, the constrained bladder would exhibit
asymmetric modes concentrated on the free (superior) dome, with nodal lines
forced to lie near the constraint boundary.

This frequency shift reinforces rather than undermines the clinical
relevance of the model.  The upward shift moves the predicted resonance
further from the ISO~2631 peak (\SIrange{4}{8}{\hertz}), deepening the
sub-resonant character of the bladder's response under occupational WBV.
However, the shifted range (\SIrange{16}{21}{\hertz}) overlaps with
frequencies produced by vibratory industrial equipment and rough-road
driving.  The free-shell predictions should be interpreted as conservative
(lower-bound) estimates; the true in-vivo frequencies are likely somewhat
higher.

\paragraph{Nonlinear elasticity.}
The exponential strain-stiffening model (equation~\ref{eq:E_fill}) is a
phenomenological fit to vibrometry data.  A hyperelastic constitutive model
(Mooney--Rivlin or Ogden) would be more physically appropriate for large
deformations, though for the small-amplitude vibrations considered here,
a linearised modulus is adequate.

\paragraph{Layered wall structure.}
The bladder wall comprises distinct layers (mucosa, submucosa, detrusor
muscle, serosa) with different mechanical properties.  The present model
uses a single effective modulus.  A multilayer shell model would capture
the bending--stretching coupling between layers, potentially modifying
both frequencies and damping.

\paragraph{Surrounding tissue.}
The bladder is embedded in the pelvic cavity, surrounded by fat, connective
tissue, and adjacent organs.  This surrounding medium would add both
damping and mass loading, likely shifting the resonant frequencies downward
and broadening the peaks.  The free-shell model therefore represents a
lower bound on frequencies with respect to boundary constraints (pelvic
contact raises frequencies) but an upper bound with respect to added-mass
effects from surrounding tissue (which would lower them).  The two effects
act in opposite directions, partially cancelling.
