\documentclass[12pt]{article}

% =============================================================================
% Packages
% =============================================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{inconsolata}
\usepackage{amsmath}
\let\Bbbk\relax
\usepackage{amssymb}

% Theorem-like environments
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newenvironment{proof}{\par\noindent\textit{Proof.}\ }{\hfill$\square$\par}

\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{lineno}

% SI units configuration
\sisetup{
  per-mode=symbol,
  group-separator={,},
}

% Line numbering (required for review submission)
\linenumbers

% =============================================================================
% Metadata
% =============================================================================
\title{Forward adequacy does not imply inverse adequacy:\\
Geometric reduction and spectral identifiability in fluid-filled elastic shells}

\author{
  Jonathan Mace\thanks{Corresponding author. E-mail: jonathanmace@microsoft.com}\\
  \small Microsoft Research, Redmond, WA, United States
  \and
  Brian R.\ Mace\\
  \small Acoustics Research Centre, Department of Mechanical and
    Mechatronics Engineering,\\
  \small University of Auckland, Auckland, New Zealand
}

\date{}

% =============================================================================
\begin{document}
% =============================================================================

\maketitle

\begin{abstract}
The resonant behaviour of fluid-filled elastic shells arises
repeatedly in biomechanics, postharvest sensing, and non-destructive
evaluation, yet each application is typically treated in isolation.
This paper advances a unifying thesis: \emph{shell geometry simultaneously
filters the forcing field, organises the modal spectrum, and determines
the invertibility of the corresponding parameter-estimation problem.}

We formalise this thesis through four formal results and a supporting
excitation proposition.
First, we prove that equivalent-radius (spherical) reductions of
non-spherical shells are \emph{rank-deficient} in the sense of
structural identifiability: geometry and material parameters become
confounded, rendering independent recovery impossible.
Second, we establish that oblate asphericity lifts this rank deficiency through
curvature-dependent mode splitting, providing the additional spectral
information needed for locally identifiable inversion.
Third, we demonstrate the corrected near-spherical asymptotics,
\(\sigma_3(\varepsilon)=\lambda_1\varepsilon^2+O(\varepsilon^4)\), so the exact
sphere is singular and the previously reported finite floor is recognised as a
discretisation artefact.
Fourth, we construct a counterexample showing that forward-model adequacy does not imply
inverse-model adequacy: an equivalent-sphere model may predict
resonant frequencies within engineering tolerance yet fail
severely when used for parameter estimation.

These formal results are supported by cross-application evidence drawn
from the human abdomen (infrasound resonance), the watermelon
(acoustic ripeness assessment), and the urinary bladder (fill-dependent
resonance).  The fourth result therefore shows that forward spectral
accuracy does not imply inverse adequacy; reduced models intended for
parameter recovery should be judged by the sensitivity structure they
preserve, not by forward error alone.
\end{abstract}

\bigskip
\noindent\textbf{Keywords:}
fluid-filled shells;
elastic shell resonance;
structural identifiability;
inverse problems;
asphericity;
Kac problem

% =============================================================================
% Sections
% =============================================================================
\input{sections/introduction}
\input{sections/background}
\input{sections/theory}
\input{sections/results}
\input{sections/discussion}
\input{sections/conclusion}

% =============================================================================
% Appendix
% =============================================================================
\input{sections/appendix}

% =============================================================================
% References
% =============================================================================
\bibliographystyle{plain}
\bibliography{references}

\end{document}
