% =============================================================================
% Conclusion
% =============================================================================
\section{Conclusion}\label{sec:conclusion}

We have studied the practical identifiability of elastic shell parameters
from resonant frequencies in the spirit of Kac's spectral question.  For the
oblate Ritz flexural model used here, the inverse problem based on the
parameter triple $(a,c,E)$ transitions smoothly from poorly conditioned at the
near-spherical limit to well conditioned at the canonical oblate operating
point.  In the context of the Browntone programme, that makes Paper~8 less a
side study than a foundation stone: it addresses the inverse question on which
the diagnostic ambitions of Papers~1--7 depend.

The main findings are:
\begin{enumerate}
  \item within the Ritz model, the condition number drops from a near-spherical
  floor value $\kappa_\mathrm{floor}\approx269$ (five modes) to
  $\kappa = 69.4$ (canonical oblate), purely through geometric eccentricity;
  \item the equivalent-sphere model is algebraically rank deficient
  (formally $\kappa = \infty$; evaluated numerically as
  $\kappa \approx 1.37 \times 10^{10}$ due to the finite-difference step),
  illustrating how model-induced degeneracy
  dwarfs the geometric effect;
  \item the smallest singular value is well described by the polynomial fit
  $\sigma_{\min} \approx \sigma_0 + \lambda_1\varepsilon^2 + \lambda_2\varepsilon^4$
  over the intermediate eccentricity range $\varepsilon\in[0.15,\,0.85]$,
  with regression intercept $\sigma_0 = 0.01113$ and shape coefficient
  $\lambda_1 = 0.00507$ (five modes); directly computed, the condition
  number approaches a finite floor $\kappa_\mathrm{floor}\approx 269$
  at $\varepsilon = 0.01$ rather than diverging;
  \item round-trip inversion recovers $(a,c,E)$ to machine precision
  ($<10^{-12}$), confirming internal consistency of the forward model and
  solver;
  \item at $1\%$ frequency noise (five modes), the Cram\'er--Rao bounds are
  approximately $\pm 22.5\%$ for $a$, $\pm 6.0\%$ for $c$, and $\pm 30.8\%$
  for $E$, comparable to existing elastographic measurement precision;
  \item the condition number remains in the range $\kappa\in[69,\,94]$ across
  measured mode counts $\mathcal{N}=3$--$9$, demonstrating robustness to
  measurement configuration (though this is not Ritz basis convergence
  evidence, since the trial-function order is held fixed);
  \item three-mode inversion is vulnerable to local minima, whereas five-mode
  inversion is robust across the tested initial guesses;
  \item a ripe-watermelon case remains well conditioned, with
  $\kappa \approx 128$.
\end{enumerate}

These results suggest a practical answer to the question posed in the title.
Within the present model, one can hear the shape of an oblate organ in the
limited but useful sense of practical local identifiability.  One cannot do so
reliably at the spherical limit.  That distinction is precisely what determines
whether a measured resonance is merely interesting or diagnostically useful.

The programme-level implication is straightforward.  If flexural resonances can
be measured reproducibly, and if the relevant parameters are identifiable, then
the spectrum becomes a non-invasive elastography tool.  For abdominal
resonance~\cite{BrowntoneCompanion}, this means that a measured modal set could
in principle constrain effective cavity geometry and wall stiffness rather than
serving only as a forward prediction.  For the bladder
problem~\cite{BrowntoneBladder}, it means that fill-dependent resonance could,
at least in principle, support inference of changing wall properties.  For
watermelon ripeness~\cite{BrowntoneWatermelon}, it explains why a tap-tone can
carry recoverable material information rather than folklore alone.

The clearest practical recommendation is equally straightforward: measure at
least five low-order flexural resonances if the goal is parameter inversion
rather than mere modal description.  Fewer modes may suffice for local tests,
but they do not provide the same robustness.

The main theoretical contribution is the three-class classification of shell
inverse problems (Section~\ref{sec:classification}): \emph{singular}
(equivalent-sphere, rank-deficient), \emph{regular bounded} (oblate Ritz,
$\kappa$ finite and generally improving with eccentricity, though with local
non-monotonicity from mode crossings in the Ritz eigenvalue branches), and
\emph{non-lifting} (prolate, $\kappa$ high and flat).  The critical finding is
that not all shape departures improve identifiability: oblate geometry benefits
from curvature--mode anti-correlation, while prolate geometry does not, because
curvature peaks and modal peaks are co-located at the poles.  This asymmetry
was not anticipated by the original power-law conjecture, which has been
replaced by the richer two-channel picture.

The most interesting open mathematical target is the closed-form derivation of
the expansion coefficients $\sigma_0$, $\lambda_1$, and $\lambda_2$ as
explicit functions of the mode set and canonical parameters
(Open Question~1, Section~\ref{sec:open_questions}).  The numerically determined
values~\eqref{eq:expansion_coeffs} already provide quantitative design rules,
but a proof would turn them into a theorem connecting geometry, modal
structure, and inverse conditioning in closed form.  That would be the crown
jewel.  For the moment, the jewel remains in the workshop.

Future work should therefore proceed in two directions.  First, the
Ritz approximation should be replaced by a full finite-element oblate shell
model to eliminate truncation error.  Second, the inversion should be tested
experimentally on phantoms and biological specimens.  Together, those steps
would move the Browntone programme from ``the resonances can be predicted'' to
``the material parameters can be recovered'', which is the more consequential
claim.
