% =============================================================================
% Discussion
% =============================================================================
\section{Discussion}\label{sec:discussion}

\subsection{Connection to Kac's question}

Kac's original problem asked whether one could infer geometry from a spectrum.
Our answer is deliberately narrower and more practical.  For the present
viscoelastic shell model, the results suggest that one \emph{can} hear the shape
of an oblate organ, in the sense that the local inverse problem for
$(a,c,E)$ is well conditioned and statistically finite.  At the spherical
limit, one cannot: the Jacobian becomes rank deficient and the Fisher matrix
loses invertibility.

The analogy with Kac should therefore be handled with care.  We do not prove a
global uniqueness theorem of the kind established by Sylvester and
Uhlmann~\cite{SylvesterUhlmann1987} for the Calder\'on inverse conductivity
problem, nor do we exclude the possibility of remote isospectral parameter sets.
Our claim is about \emph{practical identifiability} in a finite-dimensional
model relevant to measurement and inversion.  That is a less grand claim, but
also the one an experimentalist can actually use.

\subsection{Mechanism: mode-dependent curvature sampling}

The analytical results in Section~\ref{sec:theory} clarify why oblate geometry
restores identifiability.  Proposition~\ref{prop:chain_rule} shows that \emph{any}
model built on $R_\mathrm{eq} = (a^2 c)^{1/3}$ alone has a rank-deficient
Jacobian, because the chain rule forces the $a$- and $c$-columns to be exactly
proportional for all modes.  Proposition~\ref{prop:eccentricity} then shows
that the Ritz model, which integrates strain energy over the actual spheroidal
surface, introduces mode-dependent corrections at order $\varepsilon^2$.

The mechanism is \emph{mode-dependent curvature sampling}.  Different Legendre
modes $P_n(\eta)$ weight the meridional curvature gradient differently: low-order
modes sample both poles and equator broadly, while higher-order modes
concentrate energy near the equator where the curvature gradient is steepest.
This differential sampling breaks the proportionality of the $a$- and $c$-columns
and restores full rank.  The condition number diverges as
$\kappa \sim C\,\varepsilon^{-\alpha}$ as $\varepsilon \to 0$, with
theoretical exponent $\alpha=2$ and empirical estimates
$\hat\alpha\in[2.16,\,2.66]$ confirmed numerically in Section~\ref{sec:results}
(Table~\ref{tab:power_law}).

This interpretation is straightforward and does not invoke group-theoretic
symmetry breaking.  The identifiability transition is not a consequence of
reducing the symmetry group from $\mathrm{SO}(3)$ to $\mathrm{SO}(2)$; it is a
consequence of mode-dependent curvature weighting in the variational
integrals.  The distinction matters because the curvature-sampling explanation
is constructive --- it identifies the specific integrals responsible --- whereas
a symmetry-based framing would be descriptive at best and misleading at worst.

\subsection{Implications for vibroacoustic elastography}

The results are encouraging for vibroacoustic elastography and related spectral
methods.  A small number of low-order flexural resonances may contain enough
information to estimate both geometry and stiffness, provided that the operating
point is sufficiently aspherical and provided that enough modes are measured.
This is attractive because resonant frequencies are often easier to estimate
robustly than full-field mode shapes or transient wavefields.

The Cram\'er--Rao bounds give the result practical content.  At $1\%$ frequency
noise, the uncertainty in $c$ is modest, while $a$ and $E$ remain more weakly
resolved but still finite.  That anisotropy matters for experimental design:
one should not expect the same confidence in all parameters, even when the
Jacobian has full rank.

\subsection{Why model choice matters}

The most important modelling lesson is that forward-model convenience and
inverse-model usefulness are not the same thing.  A spherical reduction may be
acceptable for a rough forward estimate of resonance frequency, but it is a poor
foundation for parameter recovery.  Spherical simplifications are serviceable on
the blackboard; in inverse problems they become noticeably less cooperative.

The present study uses the oblate Ritz model for all identifiability results.
The equivalent-sphere model is retained only to illustrate the algebraic rank
deficiency of Proposition~\ref{prop:chain_rule}.  The Ritz model is itself an
approximation --- it truncates the trial function space and incurs $\sim\!8\%$
error relative to exact spheroidal shell theory --- but the mode-count
convergence of Table~\ref{tab:mode_count} shows that the identifiability
transition is robust to this truncation.  A full finite-element oblate shell
model would provide the definitive answer, but the Ritz results already
demonstrate the essential geometric mechanism.

\subsection{Relation to existing inverse methods}

Inverse vibration problems have long been studied in structural
dynamics~\cite{Gladwell2004,Gladwell2005}, and model-based elastography has
developed a wide range of optimisation and regularisation
strategies~\cite{Doyley2012}.  In acoustics and biomechanics, several studies
have estimated material parameters by fitting dynamic response models to
spectral data~\cite{Aernouts2012}.  The present contribution is more modest but
useful: before attempting a sophisticated inversion, we ask whether the chosen
measurements can, in principle, resolve the chosen parameters with acceptable
conditioning.

That perspective is valuable because poor inverse performance is often blamed on
optimisers, priors, or noise models when the underlying issue is simpler: the
Jacobian is nearly singular.  A condition-number and Fisher-information analysis
cannot solve the inverse problem by itself, but it can prevent one from asking
the data for information they do not contain.

\subsection{Local versus global identifiability}

The round-trip tests demonstrate very accurate local recovery, but global
identifiability is a separate matter.  The three-mode system is especially
vulnerable because it is exactly determined.  Local minima can occur, and a
small residual does not necessarily imply the correct parameter set when the
search is started far away.  This is why the five-mode result matters more for
practice than the machine-precision local recovery.

Whether the spectral map is globally injective --- that is, whether the oblate
shell inverse problem admits a unique solution over the full parameter domain
--- remains an open question connecting to the spectral geometry programme
initiated by Kac~\cite{Kac1966} and the perturbation theory of
Kato~\cite{Kato1966}.  The eigenvalue perturbation results of
Hald~\cite{Hald1978,Hald1984CPAM} and the shape optimisation framework of
Henrot~\cite{Henrot2006} provide relevant tools, but a proof of global
uniqueness for the present coupled fluid--shell system would require substantial
additional analysis.

Our recommendation is therefore not based on elegance but on behaviour:
\begin{itemize}
  \item use three modes only for local studies or controlled round-trip tests;
  \item use at least five flexural modes for robust inversion in realistic
  settings.
\end{itemize}

\subsection{Limitations}

Several limitations remain.
\begin{enumerate}
  \item The Ritz forward model is a variational approximation, not a full
  spheroidal shell solution.  It captures the leading eccentricity dependence
  but incurs $\sim\!8\%$ error relative to exact shell theory.  The mode-count
  convergence of Table~\ref{tab:mode_count} mitigates this concern but does
  not eliminate it entirely.
  \item The analysis is local.  We do not prove global injectivity of the map
  $(a,c,E)\mapsto \{f_n\}$.
  \item Synthetic inversion uses the same model for data generation and
  inversion.  This isolates identifiability from model-form error, but it
  means that the round-trip recovery (Section~\ref{sec:results}) is a
  verification of internal consistency, not a demonstration of real-world
  inversion capability.
  \item The mode numbers are assumed known.  In experiment, mode assignment may
  itself be uncertain.
  \item Only three parameters are estimated.  Allowing $h$, $\nu$, or fluid
  properties to vary would enlarge the parameter space and may degrade
  conditioning.
\end{enumerate}

\subsection{Future directions}

The natural next step is a full finite-element oblate shell model, which would
eliminate the Ritz truncation error and allow convergence to the exact
spheroidal solution.  Shape-calculus tools~\cite{DelfourZolesio2011} would allow
Hadamard-type Fr\'echet derivatives of the eigenvalues with respect to the
domain boundary, enabling a geometry-aware sensitivity analysis that goes beyond
the parametric approach taken here.  That would show whether the encouraging
results reported here strengthen further when the geometry is represented
exactly.  The second
priority is experimental validation, ideally first on phantoms of known
geometry and stiffness and then on biological specimens.  A Bayesian treatment,
with priors on tissue properties and uncertainty in mode identification, would
also be a useful extension.

The results suggest that geometric asymmetry plays a fundamental role in
practical identifiability of coupled fluid--shell systems, a connection that
merits further investigation using the tools of shape calculus and spectral
perturbation theory~\cite{Kato1966,Henrot2006}.

\subsection{Open Questions and Conjectures}\label{sec:open_questions}

Propositions~\ref{prop:chain_rule} and~\ref{prop:eccentricity} identify the
mechanism by which the spherical degeneracy is lifted, but they stop short of a
complete quantitative theory.  To make the outstanding mathematical programme
explicit, we record two conjectures suggested by the numerical evidence,
together with an empirical observation on mode-count scaling.
The conjectures are stated for the oblate Ritz model, since that is the setting
in which a proof would matter.  Let
$\mathcal{N}=\{n_1,\ldots,n_N\}$ denote the measured flexural mode set, let
$\varepsilon=\sqrt{1-c^2/a^2}$ be the eccentricity, and let
$\mathbf{J}_s(\varepsilon;\mathcal{N})$ denote the corresponding scaled
Jacobian of the frequency--parameter map.

\begin{conjecture}[Rate of identifiability restoration]
\label{conj:power_law}
For the Ritz model with fixed mode set $\mathcal{N}$, there exist constants
$C(\mathcal{N})>0$, $\alpha(\mathcal{N})>0$, and $\varepsilon_0>0$ such that
\begin{equation}
  \kappa\bigl(\mathbf{J}_s(\varepsilon;\mathcal{N})\bigr)
  =
  C(\mathcal{N})\,\varepsilon^{-\alpha(\mathcal{N})}\bigl(1+o(1)\bigr)
  \qquad \text{as } \varepsilon \to 0^+,
\end{equation}
where the exponent $\alpha(\mathcal{N})$ depends only on the number of modes
$N$ and on the selected mode set $\mathcal{N}$.  The theoretical prediction is
$\alpha=2$, arising from the $\varepsilon^2$ metric expansion; the empirical
estimates $\hat\alpha\in[2.16,\,2.66]$ (Table~\ref{tab:power_law}) are
consistent with this prediction to leading order.
\end{conjecture}

\begin{conjecture}[Minimum modes for identifiability]
\label{conj:min_modes}
Consider the four-parameter material map with parameter vector
\begin{equation}
  \boldsymbol{\vartheta} = (E,h,\rho_w,\rho_f)^\top,
\end{equation}
at fixed geometry and fixed $(\nu,K_f,P_\mathrm{iap})$.  The Ritz forward
model introduces three independent dimensionless groups that govern the
frequency spectrum (beyond $\varepsilon$ itself): a stiffness ratio
$Eh/K_f R$, a density ratio $\rho_w h/\rho_f R$, and a prestress ratio
$P_\mathrm{iap}/E$.  If these three groups exhaust the independent parameter
combinations (as the structure of
equations~\eqref{eq:flexural_forward}--\eqref{eq:req} suggests but we do not
formally prove), then three measured flexural modes suffice for local
identifiability if and only if $\varepsilon>0$.  At $\varepsilon=0$, the
additional proportionality constraint of Proposition~\ref{prop:chain_rule}
removes one degree of freedom, and no finite mode set yields full column rank.
This claim remains a conjecture because the completeness of the three-group
reduction has not been established rigorously; a formal proof would require
verifying that no hidden similarity scaling further reduces the effective
parameter dimension.
\end{conjecture}

\begin{remark}[Monotone improvement with mode count]
\label{rem:monotone}
The numerical evidence of Table~\ref{tab:mode_count} shows that the
Cram\'er--Rao bounds improve monotonically as the mode count $\mathcal{N}$
increases from $3$ to $9$, with diminishing marginal returns beyond
$\mathcal{N}=5$.  This is an expected consequence of overdetermination:
each additional mode adds an independent row to the Jacobian, reducing the
covariance bound.  However, we observe no clean power-law decay of $\kappa$
with $\mathcal{N}$ at fixed $\varepsilon$ --- the condition number is
non-monotone (Table~\ref{tab:mode_count}), ranging from $69.4$ at
$\mathcal{N}=5$ to $93.6$ at $\mathcal{N}=9$.  We therefore record the
improvement as an empirical observation rather than elevating it to a formal
conjecture.  The practical implication is that five modes capture the bulk
of the available information for the present three-parameter problem.
\end{remark}

Conjecture~\ref{conj:power_law} is the most tantalising of the open questions.
The numerics already suggest a clean power law with $\alpha\approx2$, but a
rigorous proof would turn a useful plot into an asymptotic theorem --- and would
give the exponent and prefactor as closed-form functions of the mode set.
That would be the crown jewel of the present identifiability programme; at
the time of writing, it remains work in progress.
