% =============================================================================
% Introduction
% =============================================================================
\section{Introduction}\label{sec:introduction}

In 1966, Kac asked the now-classic question ``Can one hear the shape of a
drum?''~\cite{Kac1966}.  The question is spectral: does the set of resonant
frequencies determine the geometry uniquely?  Gordon, Webb, and
Wolpert~\cite{Gordon1992} later showed that, for planar drums, the answer is
``no'': distinct domains can share the same Laplacian spectrum.  That result
did not close the subject.  It made it more interesting.

The Browntone programme has approached that question from the forward side.
Paper~1 established that the human abdomen supports low-order flexural
resonances in the infrasonic band~\cite{BrowntoneCompanion}; Paper~4 extended
the same fluid--shell framework to the fill-dependent resonance of the urinary
bladder~\cite{BrowntoneBladder}; and Paper~7 showed that an analogous model can
invert a watermelon tap-tone into a rind modulus estimate~\cite{BrowntoneWatermelon}.
Those papers answer variants of the question ``what frequencies does this shell
produce?''  The present paper asks the inverse question on which all such
applications ultimately depend: given measured frequencies, can one recover the
shell's material properties at all?

That identifiability question is the theoretical keystone of the programme.
Without it, a forward resonance model is descriptive but not diagnostic.  With
it, the same spectrum can become the basis of non-invasive elastography,
parameter estimation, and experimental design.  In practical terms, if a small
set of resonant frequencies determines stiffness and geometry with acceptable
conditioning, then the abdominal, bladder, and watermelon problems cease to be
curiosities of shell vibration and become inverse tools.  If not, one merely
fits a model to a spectrum that never had enough information in the first
place.

Here we therefore study an engineering analogue of Kac's inverse problem for a
fluid-filled elastic shell.  We focus on low-frequency flexural modes
$n \geq 2$, rather than the breathing mode $n=0$, which lies near
\SI{2490}{Hz} and is governed primarily by fluid compressibility.  The inverse
problem is posed on the measured flexural frequencies
$\{f_2,f_3,\ldots,f_N\}$, with the aim of recovering the semi-major axis $a$,
the semi-minor axis $c$, and the Young's modulus $E$.

The key geometric point is oblateness.  A spherical shell sits at a spectrally
degenerate limit: symmetry forces geometric sensitivities to collapse, so the
inverse map becomes singular or nearly so.  An oblate shell does not enjoy that
luxury.  Once $a \neq c$, different flexural modes sample curvature differently,
the degeneracy is lifted, and identifiability can in principle be restored.
The question is not whether asymmetry looks promising in a qualitative sense,
but whether it restores enough rank to support useful inversion.

A central modelling point must also be stated plainly.  The identifiability
analysis uses an \emph{oblate Ritz model} that integrates strain energy over
the spheroidal surface, so that each flexural mode samples meridional curvature
differently.  For comparison, we also examine the equivalent-sphere reduction
\begin{equation}
  R_\mathrm{eq} = (a^2 c)^{1/3},
\end{equation}
which collapses all curvature information into a single radius.  The
contrast between these two models illuminates the role of geometry in
identifiability: the equivalent-sphere model is algebraically rank deficient
by construction, whereas the Ritz model restores full rank for any
eccentricity $\varepsilon>0$.

Our contribution is therefore twofold.  First, we quantify practical
identifiability through the Jacobian of the frequency--parameter map, using the
dimensionless scaled Jacobian, its singular values, its condition number, and
the associated Fisher information matrix to assess whether small perturbations
in the measured frequencies can be mapped reliably back to $(a,c,E)$.  Second,
we make explicit the programme-level consequence: identifiability, not merely
forward prediction, is the mathematical foundation on which Papers~1--7 rest.
This is an analysis of \emph{practical} identifiability in the sense of Raue
et al.~\cite{Raue2009} and Wieland et al.~\cite{Wieland2021}, not a global
uniqueness theorem.

The main numerical findings are as follows.
\begin{itemize}
  \item Within the Ritz model, the condition number drops from a near-spherical
  floor value $\kappa_\mathrm{floor}\approx269$ (five modes) to
  $\kappa = 69.4$ at the canonical oblate operating point
  ($\varepsilon=0.745$), purely through geometric eccentricity.
  \item The equivalent-sphere model gives
  $\kappa = 1.37 \times 10^{10}$ (algebraically rank deficient), illustrating
  the severity of model-induced degeneracy.  By
  Proposition~\ref{prop:chain_rule}, $\kappa$ is formally infinite; the finite
  value is an artefact of the finite-difference step $\delta = 10^{-6}|\theta_j|$.
  \item The smallest singular value admits a regular two-channel expansion
  $\sigma_{\min} = \sigma_0 + \lambda_1\varepsilon^2 + O(\varepsilon^4)$;
  the curvature channel dominates everywhere ($\varepsilon_c = 1.48 > 1$).
  \item At $1\%$ frequency noise (five modes), the Cram\'er--Rao lower bounds
  correspond to uncertainties of approximately $\pm 22.5\%$ in $a$, $\pm 6.0\%$
  in $c$, and $\pm 30.8\%$ in $E$ --- comparable to existing elastographic
  precision.
  \item The identifiability metrics are robust to mode count: the condition
  number remains in the range $\kappa\in[69,\,94]$ for $\mathcal{N}=3$
  to $9$ modes.
  \item Three-mode inversion is locally feasible but exhibits local minima,
  whereas five-mode inversion is robust across the tested initial guesses.
  \item A three-class taxonomy emerges: \emph{singular} (equivalent-sphere,
  rank-deficient), \emph{regular bounded} (oblate, $\kappa$ finite and
  generally favourable, with local non-monotonicity from mode crossings), and
  \emph{non-lifting} (prolate, $\kappa$ high and flat).
  The oblate--prolate asymmetry arises from curvature--mode anti-correlation.
\end{itemize}

These results suggest that, within the present Ritz model, one can in a
practical sense hear the shape of an
oblate organ from a modest set of flexural resonances, whereas the same task is
poorly posed at the spherical limit.  For the Browntone programme, that
distinction is not a side remark.  It explains why the forward models of Papers
1--7 are potentially invertible in the first place, and why oblateness rather
than near-sphericity is the feature that turns resonance from a descriptive
quantity into a usable diagnostic observable.

The paper is organised as follows.  Section~\ref{sec:theory} summarises the
equivalent-sphere forward model and the inverse formulation.  Section
\ref{sec:methodology} describes the numerical Jacobian, the Newton-type
inversion procedure, and the parameter-space conditioning study.  Section
\ref{sec:results} presents the sphere--oblate contrast, singular-value
structure, Cram\'er--Rao bounds, and a watermelon cross-application.  Section
\ref{sec:discussion} relates the results back to Kac's question, the Browntone
applications, and vibroacoustic elastography, and presents a three-class
taxonomy of shell inverse problems that emerges from the numerics.  Section
\ref{sec:conclusion}
summarises the practical recommendations and the programme-level implications.
