\documentclass[review]{elsarticle}
\usepackage[margin=1in]{geometry}

% =============================================================================
% Packages
% =============================================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{inconsolata}
\usepackage{amsmath}
\let\Bbbk\relax
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{decorations.pathmorphing}
\usepackage{microtype}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{lineno}

% Fix duplicate page destination warning with elsarticle review mode
\hypersetup{pageanchor=false}
\AtBeginDocument{\hypersetup{pageanchor=true}}

% SI units configuration
\sisetup{
  per-mode=symbol,
  group-separator={,},
}

% Line numbering (required for JSV review submission)
\linenumbers

% =============================================================================
% Metadata
% =============================================================================
\journal{Journal of Sound and Vibration}

\begin{document}

\begin{frontmatter}

\title{Modal Analysis of a Fluid-Filled Viscoelastic Oblate Spheroidal Shell:
Implications for the Existence of the ``Brown Note''}

\author[msr]{Jonathan Mace\corref{cor1}}
\cortext[cor1]{Corresponding author}
\ead{jonathanmace@microsoft.com}

\author[auckland]{Brian R.\ Mace}
\ead{b.mace@auckland.ac.nz}

\affiliation[msr]{
  organization={Microsoft Research},
  city={Redmond, WA},
  country={United States}
}

\affiliation[auckland]{
  organization={Acoustics Research Centre, Department of Mechanical and
    Mechatronics Engineering, University of Auckland},
  city={Auckland},
  country={New Zealand}
}

\begin{highlights}
\item Upper-bound coupling disparity of $6.6\times 10^4$ explains vibration--sound asymmetry
\item Oblate spheroidal shell model predicts abdominal resonance at 4--10~Hz
\item Breathing mode at $\sim$2500~Hz; flexural modes at infrasonic frequencies
\item Airborne coupling penalised by $(ka)^n$; negligible at 120~dB SPL
\item Monte Carlo UQ confirms qualitative persistence of low-frequency modes; Sobol $S_T = 0.86$ for modulus
\end{highlights}

\begin{abstract}
Whole-body vibration at \SIrange{4}{8}{\hertz} causes well-documented
gastrointestinal disturbances, yet airborne sound at the same
frequencies does not---even at extreme intensities.  This asymmetry
underlies the persistent ``brown note'' hypothesis: the conjecture that
infrasonic sound can induce involuntary defecation.  We resolve the
asymmetry by modelling the human abdomen as a fluid-filled viscoelastic
oblate spheroidal shell and quantifying both excitation pathways within
a common energy-budget framework.

The model predicts flexural modes ($n \geq 2$) at \SIrange{4}{10}{\hertz},
consistent with ISO~2631 abdominal resonance data.  At these frequencies the
abdomen lies deep in the Rayleigh regime ($ka \approx 0.01$); the resulting
$(ka)^n$ penalty and air--tissue impedance mismatch reduce airborne coupling
by four orders of magnitude.  Energy-consistent analysis yields wall
displacements of \SI{0.014}{\micro\metre} at \SI{120}{\decibel}
SPL---far below cellular mechanotransduction benchmarks.  Mechanical vibration at
$a_\mathrm{rms} = \SI{0.1}{\metre\per\second\squared}$ produces
displacements approximately $6.6 \times 10^4$ times larger (SDOF upper
bound, $\Gamma_2 = 1$).  Monte Carlo analysis spanning representative anatomical variability
confirms the qualitative persistence of the coupling disparity across the
parameter space, with the fundamental flexural frequency varying between
3 and \SI{16}{\hertz} (90\% credible interval, median \SI{6.4}{\hertz};
$S_T = 0.86$ for elastic modulus); the coupling ratio represents an upper
bound from the single-degree-of-freedom idealisation.  The global abdominal-cavity resonance is
physically real, but airborne sound at any plausible intensity cannot
excite the global cavity resonance to physiologically relevant
amplitudes.
\end{abstract}

\begin{keyword}
fluid-filled shell vibration \sep viscoelastic oblate spheroid \sep
infrasound \sep whole-body vibration \sep acoustic--structural coupling \sep
ISO~2631
\end{keyword}

\end{frontmatter}

% =============================================================================
% Section 1: Introduction
% =============================================================================
\input{sections/introduction}

% =============================================================================
% Section 2: Mathematical Formulation (the core contribution)
% =============================================================================
\input{sections/section2_formulation}

% =============================================================================
% Section 3: Parametric Study
% =============================================================================
\input{sections/results}

% =============================================================================
% Section 4: Coupling Comparison (key novel result)
% =============================================================================
\input{sections/section4_coupling}

% =============================================================================
% Section 5: Discussion
% =============================================================================
\input{sections/discussion}

% =============================================================================
% Section 6: Conclusions
% =============================================================================
\input{sections/conclusion}

% =============================================================================
% References
% =============================================================================
\bibliographystyle{elsarticle-num}
\bibliography{references}

% =============================================================================
% Data Availability & CRediT
% =============================================================================
\section*{Data availability}
All analytical models and computational scripts used in this study are
available in the accompanying repository.

\section*{CRediT authorship contribution statement}
\textbf{Jonathan Mace}: Conceptualization, Methodology, Formal Analysis,
Software, Writing -- Original Draft, Writing -- Review \& Editing.
\textbf{Brian R.\ Mace}: Methodology, Validation, Writing -- Review \& Editing.

\section*{Acknowledgements}
The authors thank an anonymous colleague for a constructive pre-submission
review that improved the clarity of the manuscript.

\section*{Declaration of generative AI and AI-assisted technologies in the
writing process}
During the preparation of this work the authors used GitHub Copilot (GitHub,
Inc.; powered by large language models from OpenAI and Anthropic) in order to
assist with: (1)~implementing analytical expressions as Python code for
numerical evaluation, (2)~generating publication figures from computed results,
(3)~conducting structured literature searches, and (4)~drafting and revising
manuscript text.  After using this tool, the authors reviewed and edited the
content as needed and take full responsibility for the content of the
publication.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests
or personal relationships that could have appeared to influence the work
reported in this paper.

\end{document}
