\documentclass[review]{elsarticle}
\usepackage[margin=1in]{geometry}

% =============================================================================
% Packages
% =============================================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{inconsolata}
\usepackage{amsmath}
\let\Bbbk\relax
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{lineno}

% Fix duplicate page destination warning with elsarticle review mode
\hypersetup{pageanchor=false}
\AtBeginDocument{\hypersetup{pageanchor=true}}

% SI units configuration
\sisetup{
  per-mode=symbol,
  group-separator={,},
}

% Line numbering (required for review submission)
\linenumbers

% =============================================================================
% Metadata
% =============================================================================
\journal{Postharvest Biology and Technology}

\begin{document}

\begin{frontmatter}

\title{Can You Hear the Ripeness? Non-Destructive Acoustic Assessment of
Fruit Maturity via Shell Resonance Inversion}

\author[msr]{Jonathan Mace\corref{cor1}}
\cortext[cor1]{Corresponding author}
\ead{jonathanmace@microsoft.com}

\author[auckland]{Brian R.\ Mace}
\ead{br.mace@auckland.ac.nz}

\affiliation[msr]{
  organization={Microsoft Research},
  city={Redmond, WA},
  country={United States}
}

\affiliation[auckland]{
  organization={Acoustics Research Centre, Department of Mechanical and
    Mechatronics Engineering, University of Auckland},
  city={Auckland},
  country={New Zealand}
}

\begin{abstract}
The `thump test''---tapping a watermelon and listening for
ripeness---is practised worldwide but lacks a quantitative physical
model.  We model the watermelon as a fluid-filled viscoelastic oblate
spheroidal shell and derive an analytical expression for the tap-tone
natural frequency $f_2$ as a function of rind thickness, elastic
modulus, fruit geometry, and flesh density.  Sobol sensitivity analysis
reveals that the rind elastic modulus $E_{\mathrm{rind}}$ dominates the
frequency response (total-order index $S_T > 0.5$).  Because $f_2^2$
is exactly linear in $E_{\mathrm{rind}}$ when turgor pressure is
negligible, the forward model admits a closed-form inversion: a single
tap-tone measurement yields the rind modulus, which correlates with
ripeness through pectin degradation.  We construct a universal
dimensionless ripeness parameter $\Pi_{\mathrm{ripe}}$ that collapses
predictions across cultivars (Crimson Sweet, Sugar Baby, Charleston
Gray, seedless) onto a single master curve.  Predictions are validated
against published resonance measurements on melons.  The framework
generalises directly from prior work on biological cavities,
demonstrating that the same shell theory governs both biomedical
vibroacoustics and agricultural non-destructive evaluation.
\end{abstract}

\begin{keyword}
watermelon \sep acoustic testing \sep non-destructive evaluation \sep
shell theory \sep ripeness \sep inverse problem
\end{keyword}

\end{frontmatter}

% =============================================================================
% Section 1: Introduction
% =============================================================================
\input{sections/introduction}

% =============================================================================
% Section 2: Mathematical Formulation
% =============================================================================
\input{sections/formulation}

% =============================================================================
% Section 3: Results
% =============================================================================
\input{sections/results}

% =============================================================================
% Section 4: Validation
% =============================================================================
\input{sections/validation}

% =============================================================================
% Section 5: Discussion
% =============================================================================
\input{sections/discussion}

% =============================================================================
% Section 6: Conclusions
% =============================================================================
\input{sections/conclusion}

% =============================================================================
% References
% =============================================================================
\bibliographystyle{elsarticle-num}
\bibliography{references}

% =============================================================================
% Data Availability & CRediT
% =============================================================================
\section*{Data availability}
All analytical models and computational scripts used in this study are
available in the accompanying repository at
\url{https://github.com/JonathanMace/brownnote}.

\section*{CRediT authorship contribution statement}
\textbf{Jonathan Mace}: Conceptualization, Methodology, Software, Supervision,
Writing -- Original Draft, Writing -- Review \& Editing.
\textbf{Brian R.\ Mace}: Writing -- Review \& Editing, Validation.

\section*{Acknowledgements}
Portions of the analytical derivation, code development, and manuscript
drafting were assisted by GitHub Copilot (GitHub, Inc.), a large language
model operating under human supervision.  All technical content was
independently verified by the authors.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests
or personal relationships that could have appeared to influence the work
reported in this paper.

\end{document}
