\section{Introduction}
\label{sec:introduction}

% --- The thump test as universal folklore ------------------------------------

Every summer, shoppers worldwide perform an instinctive acoustic
experiment: they tap a watermelon with their knuckles and listen.  A
deep, resonant thump signals ripeness; a dull thud suggests an
under-ripe fruit; a hollow ring warns that the flesh has turned mealy.
This `thump test'' is remarkably consistent across cultures, yet it has
never been given a quantitative physical model that connects the tap-tone
frequency to the measurable mechanical properties of the fruit.

% --- Existing empirical work -------------------------------------------------

Yamamoto et al.~\cite{Yamamoto1980} pioneered the acoustic impulse
response method and included early measurements on watermelons.
Subsequent watermelon-specific studies confirmed that low-frequency
impact and vibration signatures carry useful information about internal
quality.  Stone et al.~\cite{Stone1996} reported early nondestructive
quality assessment based on acoustic response, Diezma-Iglesias et
al.~\cite{DiezmaIglesias2004} used impact acoustics to detect internal
quality differences in seedless fruit, Sadrnia et
al.~\cite{Sadrnia2008Vibration} predicted watermelon quality from
vibration signals, and Mao et al.~\cite{Mao2016} related vibrational
characteristics directly to firmness.  In parallel, the broader fruit
acoustics literature established the acoustic impulse technique as a
practical firmness metric across multiple species, including Conference
pears~\cite{Schotte1999, DeBelieetal2000, Zude2006}, while wider reviews
placed such methods within the postharvest sensing toolbox
\cite{Abbott1997}.  From an engineering standpoint, these approaches sit
comfortably within the broader family of acoustic non-destructive
testing methods, in which transient responses are used to infer internal
condition~\cite{GrosseOhtsu2008}.  The common weakness is that the
observable is informative but not explained: frequency or spectral
features are correlated with firmness or maturity, yet the governing
structural mechanics remain implicit.

% --- The gap: no physics-based shell model -----------------------------------

What is missing is a first-principles model that treats the fruit as what
it physically is: a fluid-filled viscoelastic shell.  Unlike purely
empirical correlations, we derive a closed-form analytical relationship
between the tap-tone frequency and the measurable mechanical and
geometric properties of the fruit.  The relationship does not merely fit
data; it explains why stiffness, rind thickness, size, and fluid loading
shift the resonance, and---crucially---it admits an \emph{inversion} from
a single measured frequency to the elastic modulus of the rind.

% --- Connection to prior work on biological cavities -------------------------

The mathematical ingredients for this problem are standard.  Classical
shell theory provides the flexural scaling and modal structure
\cite{Leissa1973, Soedel2004}, while fluid-loaded acoustics supplies the
added-mass interpretation for a shell coupled to an enclosed fluid
\cite{MorseIngard1968, Junger1986}.  In our companion papers, we modelled
the human abdomen as a fluid-filled oblate spheroidal shell and derived
closed-form expressions for its modal frequencies.  The watermelon
presents a structurally analogous problem---an oblate spheroid with a
thin elastic rind enclosing a near-incompressible fluid---albeit with
different material parameters and a far more appetising motivation.

% --- Mark Kac and the inverse problem ----------------------------------------

The title of this paper echoes Kac's celebrated question, `Can one hear
the shape of a drum?''~\cite{Kac1966}.  We pose a related but distinct
inverse problem: \emph{Can one hear the ripeness of a watermelon?}  We
show that the answer is yes, at least for the dominant flexural mode
$n = 2$, and that the inversion admits a closed-form solution.

% --- Contribution and paper outline ------------------------------------------

In this paper, we:
\begin{enumerate}
  \item derive the tap-tone eigenfrequency $f_2$ for a fluid-filled
    oblate spheroidal shell parameterised by rind thickness, elastic
    modulus, geometry, and flesh density;
  \item perform Sobol sensitivity analysis to identify the dominant
    parameter (the rind elastic modulus $E_{\mathrm{rind}}$);
  \item exploit the linearity of $f_2^2$ in $E_{\mathrm{rind}}$ to
    construct a closed-form inversion from a single tap-tone measurement;
  \item introduce a dimensionless geometric invariant
    $\Pi_{\mathrm{ripe}}$ that collapses cultivar-dependent predictions
    onto a single calibration constant; and
  \item benchmark the model against published resonance measurements on
    watermelons and other fruits.
\end{enumerate}

The remainder of the paper is organised as follows.
Section~\ref{sec:formulation} presents the mathematical formulation.
Section~\ref{sec:results} gives the forward model predictions, Sobol
analysis, and universal curve.  Section~\ref{sec:validation} compares
predictions with published data.  Section~\ref{sec:discussion}
discusses the physical interpretation and practical implications.
Section~\ref{sec:conclusion} concludes.
