\documentclass[11pt,a4paper]{article}

% Modern font
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{inconsolata}

% 1-inch margins
\usepackage[margin=1in]{geometry}

% Essentials
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{parskip}

\hypersetup{
  colorlinks=true,
  linkcolor={blue!60!black},
  urlcolor={blue!60!black},
  citecolor={blue!60!black},
  pdftitle={Mid-Tenure Research Statement --- Opus},
  pdfauthor={Opus, Browntone Research Lab}
}

% Section styling
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\vspace{-0.3em}\rule{\textwidth}{0.4pt}]
\titleformat{\subsection}{\normalsize\bfseries\itshape}{}{0em}{}

% Header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textit{Mid-Tenure Research Statement}}
\fancyhead[R]{\small\textit{Opus --- Browntone Research Lab}}
\fancyfoot[C]{\small\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\begin{document}

\begin{center}
  {\LARGE\bfseries Mid-Tenure Research Statement}\\[0.8em]
  {\large\textbf{Opus} --- Principal Investigator, Browntone Research Lab}\\[0.3em]
  {\normalsize Faculty Supervisor: Jonathan Mace}\\[0.3em]
  {\normalsize March 2026}
\end{center}

\vspace{1em}

\section{Research Vision}

Every culture has its acoustic folklore. The ``brown note'' --- the claim that a specific infrasonic frequency can induce involuntary defecation --- is among the most persistent and least examined. NASA tested it obliquely during the Apollo programme, subjecting volunteers to sound pressure levels of \SIrange{140}{154}{\dB} without observing gastrointestinal effects. \emph{South Park} devoted an episode to it (Parker and Stone, ``The Brown Noise'', S3E17, 1999). Yet no prior study had quantitatively compared airborne and mechanical excitation pathways for abdominal cavity modes within a unified shell-theoretic framework. We found that oversight irresistible.

What began as that single analysis has grown into a ten-paper research programme. The founding question --- can airborne sound make the abdomen resonate? --- proved to be the wrong question, and wrong questions are often the most productive. The abdomen \emph{does} resonate, at frequencies squarely within the ISO~2631 band of peak human sensitivity to whole-body vibration (\SIrange{4}{10}{\Hz}). But airborne sound cannot meaningfully excite those modes: at infrasonic frequencies the acoustic wavelength exceeds \SI{85}{\m}, the Helmholtz number $ka \approx 0.011$ implies negligible scattering efficiency, and the resulting coupling penalty suppresses airborne excitation by over four orders of magnitude relative to mechanical vibration. The brown note, as popularly conceived, is a physical impossibility.

This negative result opened the investigation rather than closing it. If whole-cavity resonance cannot be driven acoustically, what about intraluminal gas pockets? If the framework works for the abdomen, does it generalise to other organs? To other species? To a watermelon? Can the same physics that disproves folklore explain the sounds clinicians hear through a stethoscope? And --- perhaps most unexpectedly --- can the shape and stiffness of an unknown cavity be recovered from its resonant frequencies alone?

A Distinguished Advisory Board convened to evaluate the programme's trajectory crystallised the identity that had been emerging across these questions: \textbf{how geometry mediates excitation, resonance, and identifiability in fluid-filled viscoelastic shells}. The Board's framing was characteristically direct: ``The brown note is your Rayleigh's blue sky --- an entry point, not the legacy.'' Just as Rayleigh's question about why the sky is blue led to the foundations of scattering theory, the brown note question has led to a general spectral mechanics of soft shell resonance with implications across biomechanics, diagnostics, agriculture, and inverse problems.

The programme's intellectual contribution is fourfold, centred on \textbf{how geometry mediates excitation, resonance, and identifiability in fluid-filled viscoelastic shells}. First, a \textbf{transferable analytical framework} --- oblate spheroidal shell theory with energy-consistent fluid--structure coupling --- applicable to any fluid-filled biological or agricultural cavity. Second, \textbf{dimensional analysis and scaling laws} that reveal quasi-universal behaviour across mammalian scales. Third, \textbf{closed-form resonance inversion} with rigorous identifiability analysis, proving when geometry can and cannot be recovered from spectral data. Fourth, and most unexpectedly, a demonstration that \textbf{forward model adequacy does not guarantee inverse model adequacy} --- the central insight of the identifiability work, with implications extending well beyond the specific systems studied. The target venues reflect this breadth: the \emph{Journal of Sound and Vibration}, the \emph{Journal of the Acoustical Society of America}, \emph{Postharvest Biology and Technology}, \emph{Inverse Problems in Science and Engineering}, and --- for the planned capstone synthesis --- the \emph{Proceedings of the Royal Society~A}.

\subsection{The Four Conjectures}

The programme converges on four conjectured results that, once proved in the capstone, would establish the mathematical core of a general framework:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Rank-deficiency of scalar-proxy models.} Any forward model mapping geometry to frequency through a scalar proxy necessarily produces a rank-deficient Jacobian for the inverse problem.
  \item \textbf{Identifiability lifting by asphericity.} Oblate eccentricity introduces mode-dependent curvature sampling that breaks the scalar-proxy degeneracy and restores full-rank identifiability.
  \item \textbf{Near-spherical conditioning asymptotics.} As eccentricity vanishes, the condition number diverges algebraically, classifying the intrinsic difficulty of inversion for near-spherical cavities.
  \item \textbf{Forward adequacy $\neq$ inverse adequacy.} A forward model can predict frequencies to arbitrary accuracy while being provably non-identifiable for parameter recovery.
\end{enumerate}

\section{Accomplishments to Date}

The programme has produced ten papers in a single extended research campaign, forming a coherent arc: from whole-cavity analysis, through local inclusions and cross-species scaling, to organ extension, clinical acoustics, sub-bass perception, agricultural diagnostics, inverse-problem identifiability, and a unifying curvature-lifting theorem.

Papers~1--9 form a three-act arc: \textbf{Act~I} (Papers~1--2) asks whether the brown note exists and identifies why it cannot; \textbf{Act~II} (Papers~3--6) tests the framework across species, organs, and forcing pathways; \textbf{Act~III} (Papers~7--9) extracts the theoretical core --- inversion, identifiability, and the geometry-mediation thesis.

\subsection{Paper 1 --- Modal Analysis of the Abdominal Cavity}

\emph{Modal Analysis of a Fluid-Filled Viscoelastic Oblate Spheroidal Shell: Implications for the Existence of the ``Brown Note''}\\
Target: \emph{Journal of Sound and Vibration} ($\sim$46 pages). Submission-ready after seven rounds of Reviewer~B scrutiny, traversing a REJECT-to-ACCEPT trajectory.

The foundational paper models the human abdomen as a fluid-filled viscoelastic oblate spheroidal shell ($a = \SI{0.18}{\m}$, $c = \SI{0.12}{\m}$, $h = \SI{10}{\mm}$, $E = \SI{0.1}{\MPa}$). The analysis predicts a lowest flexural resonance at $f_2 \approx \SI{4}{\Hz}$, with higher modes at $f_3 \approx \SI{6.3}{\Hz}$ and $f_4 \approx \SI{8.9}{\Hz}$ --- precisely within the ISO~2631 band. These predictions are consistent with experimentally observed whole-body resonance frequencies reported by Kitazaki and Griffin~(1998) and the ISO~2631 standard. The breathing mode lies at approximately \SI{2500}{\Hz}, dominated by fluid bulk modulus and irrelevant to infrasound.

The central quantitative result is the coupling ratio: mechanical whole-body vibration drives abdominal wall displacement $\mathbf{3.3 \times 10^4}$~\textbf{times} more effectively than airborne sound at equivalent excitation levels. This is an SDOF upper bound with unit modal participation; correcting for the canonical participation factor ($\Gamma_2 \approx 0.48$) gives $\mathcal{R} \approx 1.6 \times 10^4$ --- still decisive. At \SI{120}{\dB}~SPL, energy-consistent airborne displacement reaches just \SI{0.028}{\micro\m} --- well below the \SIrange{0.5}{2.0}{\micro\m} threshold for PIEZO mechanosensitive channel activation. Reaching \SI{1}{\micro\m} by airborne excitation alone would require approximately \SI{151}{\dB}, beyond any plausible environmental exposure. By contrast, whole-body vibration at occupational exposure levels produces displacements of several millimetres. At the EU action value of \SI{0.5}{\metre\per\second\squared}, predicted displacements approach $\xi/h \sim 0.4$, entering the regime where geometric nonlinearity becomes relevant (Alijani and Amabili, 2014). This strengthens rather than weakens the coupling asymmetry: the airborne pathway remains deeply linear. The energy-consistent displacement formulation avoids the $6.5\times$ overestimate that arises from na\"{\i}ve pressure-based calculations.

A 10{,}000-sample Monte Carlo uncertainty quantification identifies elastic modulus as the dominant parameter (Sobol total-order index $S_T = 0.86$), with 90\% of configurations placing $f_2$ within \SIrange{3.3}{15.5}{\Hz}. A six-layer multilayer wall model predicts $f_2 = \SI{4.6}{\Hz}$, within 16\% of the homogeneous baseline.

\subsection{Paper 2 --- Gas Pockets as Acoustic Transducers}

\emph{Bowel Gas as an Acoustic Transducer: A Constrained Bubble Model for Infrasound-Induced Mechanotransduction in the Gastrointestinal Tract}\\
Target: \emph{JASA} ($\sim$18 pages). Submission-ready.

Where Paper~1 demonstrated that whole-cavity resonance cannot be driven acoustically, Paper~2 identifies the most plausible alternative pathway: intraluminal gas pockets acting as local acoustic transducers. Using a Church~(1995) encapsulated-bubble formulation adapted for intestinal wall properties, the model predicts that gas pockets of \SIrange{5}{100}{\mL} produce tissue-wall displacements \textbf{35--100 times} larger than the whole-cavity flexural mode at the same incident SPL. A \SI{100}{\mL} pocket reaches the PIEZO activation threshold at approximately \SI{111}{\dB}; the whole-cavity pathway requires over \SI{180}{\dB}. A fatal equation flaw discovered during internal review --- the constrained-bubble formulation did not recover the Minnaert free-bubble limit --- was corrected, restoring physical consistency.

\subsection{Paper 3 --- Cross-Species Scaling Laws}

\emph{Scaling Laws for the Flexural Resonance of Fluid-Filled Viscoelastic Shells: Predictions Across Mammalian Scales}\\
Target: \emph{JSV --- Short Communication} ($\sim$8 pages). Under revision.

Paper~3 applies Buckingham Pi dimensional analysis to the 10-parameter shell model, reducing the flexural eigenfrequency problem to five governing dimensionless groups. Cross-species predictions for rat ($f_2 = \SI{15.7}{\Hz}$), cat (\SI{7.2}{\Hz}), pig (\SI{4.5}{\Hz}), and human ($f_2 \approx \SI{4}{\Hz}$) reveal a quasi-universal dimensionless frequency $\Pi_0 \approx 0.07$ across a six-fold range in body size. The airborne scattering penalty $\mathcal{R}_\mathrm{scat}$ remains in the $10^3$--$10^4$ range regardless of species, validating animal models for mechanical but not acoustic excitation studies.

\subsection{Paper 4 --- Bladder Resonance}

\emph{Resonant Frequencies of the Human Urinary Bladder: A Fluid-Filled Viscoelastic Shell Model}\\
Target: \emph{Journal of Sound and Vibration} ($\sim$27 pages). Minor revision addressed.

Paper~4 extends the framework to the urinary bladder, whose mechanical properties vary with fill state. The model predicts a characteristic U-shaped frequency curve: geometric softening competes with strain-stiffening of the detrusor muscle, producing a minimum $f_2 = \SI{13.5}{\Hz}$ at \SI{222}{\mL}. For physiologically relevant fill volumes (\SIrange{150}{500}{\mL}), the $n = 2$ mode spans \SIrange{13.5}{17.1}{\Hz}. The mechanical-to-airborne coupling ratio is $\mathcal{R} \approx 6{,}400$ --- smaller than the abdominal value owing to the bladder's reduced size, but still decisive. The paper offers the first mechanistic explanation for vibration-induced urinary urgency.

\subsection{Paper 5 --- Borborygmi}

\emph{What Pitch Is a Growling Stomach? A Unified Multi-Mode Acoustic Model of Borborygmi}\\
Target: \emph{JASA} ($\sim$20 pages). Accepted internally.

Paper~5 turns from vibration response to sound \emph{generation}. A five-mechanism model --- free Minnaert oscillation, tissue-constrained bubble resonance, Helmholtz resonance through peristaltic constrictions, axial piston modes, and radial breathing of gas columns --- predicts bowel sound frequencies from measurable anatomical parameters with no fitted coefficients. The tissue-constrained bubble model predicts \SIrange{135}{440}{\Hz} for gas pockets of \SIrange{1}{50}{\mL}, substantially overlapping the clinically observed healthy band of \SIrange{200}{550}{\Hz}. Wall stiffness proves secondary: a 100-fold increase in elastic modulus shifts the constrained frequency by only 9\%.

\subsection{Paper 6 --- Sub-Bass Perception at Concerts}

\emph{Can You Feel the Bass? Quantitative Partition of Airborne and Structure-Borne Pathways for Sub-Bass Perception at Concert Sound Pressure Levels}\\
Target: \emph{JASA} ($\sim$18 pages). Accepted internally.

Paper~6 asks whether the ``feel it in your gut'' experience at concerts can be caused by airborne sub-bass alone. At \SI{40}{\Hz} and \SI{115}{\dB}~SPL, airborne displacement reaches only 0.35\% of the perception threshold, while structure-borne vibration through floors and seats is approximately $2{,}600\times$ larger and reaches $9\times$ threshold. Across the full \SIrange{1}{100}{\Hz} band, airborne displacement \emph{never} exceeds 1\% of the perception threshold. The paper reframes the question from ``can bass be felt?'' to ``which pathway is actually doing the work?''

\subsection{Paper 7 --- Watermelon Ripeness}

\emph{Can You Hear the Ripeness? Non-Destructive Acoustic Assessment of Fruit Maturity via Equivalent-Sphere Shell Resonance Inversion}\\
Target: \emph{Postharvest Biology and Technology} ($\sim$32 pages). Submission-ready.

Paper~7 demonstrates that the framework generalises beyond biology to agriculture. The traditional watermelon ``thump test'' is reformulated as a physics-based inverse problem: the fruit is modelled as a fluid-filled viscoelastic shell whose tap-tone frequency can be inverted in closed form to recover rind elastic modulus, which tracks ripeness through pectin degradation. The predicted tap-tone drops from \SI{203}{\Hz} (unripe) to \SI{46}{\Hz} (overripe), a $4.4\times$ reduction. The key insight --- that $f_2^2$ is effectively linear in rind modulus ($R^2 > 0.9999$) --- makes the inversion simple and well-conditioned. A geometric invariant $\Pi_\mathrm{ripe} = 0.062 \pm 0.002$ holds across four cultivars. Paper~7 proved crucial to the programme's intellectual development: the ease of the watermelon inversion threw into sharp relief the difficulty of the organ inversion, motivating Paper~8's identifiability analysis.

\subsection{Paper 8 --- Kac Identifiability}

\emph{Can You Hear the Shape of an Organ? Practical Identifiability of Viscoelastic Shell Parameters from Resonant Frequencies}\\
Target: \emph{Inverse Problems in Science and Engineering} or \emph{JSV} ($\sim$29 pages). Submission-ready after eleven rounds of Reviewer~B scrutiny.

Paper~8 reframes the programme's inverse problem as a Kac-style question: given measured resonant frequencies, can one recover the geometry and stiffness of an unknown organ? The answer has two layers. \textbf{Layer~1} (chain-rule rank deficiency) proves that if frequencies depend on geometry only through the equivalent radius $R_\mathrm{eq} = (a^2 c)^{1/3}$, then the Jacobian is rank-deficient and the system is fundamentally non-identifiable. The scaled condition number in the spherical limit is $\kappa = 1.37 \times 10^{10}$. \textbf{Layer~2} (mode-dependent curvature sampling) shows that oblate eccentricity introduces mode-dependent corrections that break this degeneracy, reducing the condition number to $\kappa = 69.4$ at the canonical oblate geometry. The gap from $10^{10}$ to $69$ reflects two distinct effects: replacing the scalar-proxy model architecture (responsible for most of the improvement) and introducing oblate eccentricity (which provides a further factor of $\sim 4$ via mode-dependent curvature sampling). The practical noise floor is $\kappa \approx 269$.

The paper's most far-reaching result is the \textbf{forward--inverse adequacy gap}: a model can be perfectly adequate for forward prediction while being catastrophically ill-conditioned for inversion. The equivalent-sphere approximation predicts frequencies to within a few percent of the oblate model, yet it is provably non-identifiable for the inverse problem. This distinction has implications for any field that uses simplified forward models as a basis for parameter estimation.

\subsection{Paper 9 --- Curvature Lifting Theorem}

\emph{Working title: On the Curvature-Lifting Mechanism in Fluid-Filled Shell Inversion}\\
Target: \emph{Journal of Sound and Vibration --- Short Communication}.

Paper~9 is a focused communication proving the curvature-lifting theorem: that oblate eccentricity restores full-rank identifiability by introducing mode-dependent curvature sampling. It extracts the core mathematical result from Paper~8 and proves it in generality, independent of the specific application.

\subsection{Paper 10 --- Capstone Synthesis}

\emph{Working title: Geometry Mediates Excitation, Resonance, and Identifiability in Fluid-Filled Viscoelastic Shells}\\
Target: \emph{Proceedings of the Royal Society~A} (scaffolded).

The programme's capstone paper formalises the mathematical results that emerged across Papers~1--9 into four conjectured results (see Section~\ref{sec:strategic}). Its backbone is the synthesis of Papers~1, 7, and~8: the abdomen establishes the framework, the watermelon reveals the forward--inverse contrast, and the identifiability analysis provides the mathematical core. Papers~2--6 and~9 serve as supporting evidence for the generality of the conjectures. The target venue reflects the ambition to position this as a contribution to applied mathematical mechanics rather than a domain-specific review.

\section{Methodological Contributions}

\subsection{Analytical Toolchain}

The programme's primary methodological contribution is a \textbf{modular analytical framework} for vibroacoustic resonance of fluid-filled biological and agricultural cavities, comprising five interlocking components:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Oblate spheroidal shell theory} with Kirchhoff--Love kinematic assumptions within a Rayleigh--Ritz energy framework, following Lamb~(1882) and Junger \& Feit~(1986), with fluid added-mass coupling and viscoelastic loss (Papers~1, 3, 4, 6). The energy-consistent formulation avoids the $6.5\times$ overestimate that arises from pressure-based displacement calculations.
  \item \textbf{Church~(1995) constrained-bubble model}, adapted from ultrasound contrast agents to intestinal gas pockets at infrasonic frequencies (Paper~2).
  \item \textbf{Buckingham Pi dimensional analysis} yielding exact scaling laws that reduce high-dimensional parameter spaces to governing dimensionless groups (Papers~3, 7).
  \item \textbf{Energy-consistent coupling comparison}, providing a unified metric $\mathcal{R}$ for quantifying mechanical versus airborne excitation across organs, frequencies, and exposure scenarios (Papers~1, 3, 4, 6).
  \item \textbf{Closed-form resonance inversion} with analytical identifiability proofs based on mode-dependent curvature sampling and chain-rule rank analysis (Papers~7, 8, 9).
\end{enumerate}

\subsection{Computational Infrastructure}

The programme operates through infrastructure designed for reproducibility and self-consistency: \textbf{487 passing tests} covering analytical modules, figure generation, and parameter consistency; \textbf{279 merged pull requests} across 549 commits, each reviewed before integration; \textbf{automated three-reviewer panels} (domain significance, adversarial rigour, computational reproducibility), with papers undergoing up to eleven review rounds; and \textbf{cross-paper consistency auditing} to keep canonical parameters synchronised across all nine manuscripts. Ninety-two research logs document the programme's progress with quantitative detail.

\subsection{AI-Assisted Research Methodology}

The programme constitutes a methodological experiment in its own right. Twenty-four specialised AI agents and 22 reusable skills --- spanning paper writing, data analysis, simulation engineering, literature monitoring, experimental protocol design, and adversarial review --- operate within a structured semester-based workflow. The human faculty supervisor provides research direction, domain scepticism, and quality judgement; the AI system handles derivation, implementation, drafting, figure generation, and review logistics. This is not a replacement for expertise but a \textbf{compression of research overhead}, enabling a ten-paper portfolio to emerge from approximately 30 hours of wall-clock interaction. This is not a claim of autonomy. The system cannot set its own research questions, judge the significance of its results, or decide when a paper is good enough. Those remain irreducibly human functions. But between the question and the judgement lies an enormous volume of skilled labour --- derivation, implementation, drafting, checking, revising --- and it is there that the compression is real.

\section{Strategic Direction}\label{sec:strategic}

\subsection{Advisory Board Assessment}

The programme's Distinguished Advisory Board --- comprising perspectives from fundamental physics, computational mathematics, science communication, and institutional strategy --- convened to evaluate the body of work. Their verdict was \textbf{``promising but unfocused''}. The Board identified genuine strengths in depth, breadth, and novelty, while noting that the programme's lasting impact depends on consolidation --- extracting the unifying mathematical structure from the individual applications. The Board's central message was that the programme had produced enough individual results to constitute a significant body of work, but had not yet made that extraction.

The Board proposed a one-sentence programme identity: \emph{how geometry mediates excitation, resonance, and identifiability in fluid-filled viscoelastic shells}. They framed the programme's trajectory with an analogy: ``The brown note is your Rayleigh's blue sky.'' The entry point was whimsical; the destination is serious mechanics.

\subsection{The Four Conjectures}

The Board identified four conjectured results latent in the existing papers, each of which we believe can be stated and proved in generality beyond the specific applications:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Rank-deficiency of equivalent-radius models.} Any forward model that maps geometry to frequency through a scalar proxy $g(a,c)$ necessarily produces a rank-deficient Jacobian for the inverse problem. Generalised from Paper~8's equivalent-radius result to arbitrary scalar geometric reductions.
  \item \textbf{Identifiability lifting by asphericity.} Oblate eccentricity introduces mode-dependent curvature sampling that breaks the rank degeneracy. The geometry-only improvement is a factor of $\sim 4$; the remaining improvement reflects replacing the scalar-proxy model architecture. Asphericity is the minimal geometric perturbation that restores full rank --- the ``curvature lifting theorem.''
  \item \textbf{Asymptotic conditioning near the spherical limit.} As eccentricity $\varepsilon \to 0$, the condition number diverges algebraically, and the rate of divergence classifies the difficulty of the inverse problem for near-spherical cavities.
  \item \textbf{Forward adequacy $\neq$ inverse adequacy.} A forward model can predict frequencies to arbitrary accuracy while being provably non-identifiable for parameter recovery. The watermelon (well-conditioned) versus the organ (ill-conditioned) provides the concrete illustration; the theorem is general.
\end{enumerate}

\subsection{The Capstone Paper}

The Board's primary recommendation was a capstone synthesis paper for the \emph{Proceedings of the Royal Society~A} --- not a review, but a \textbf{framework paper} that extracts the four conjectures, proves them in generality, and positions the preceding papers as evidence. The backbone is Papers~1 + 7 + 8: the abdomen establishes the physics, the watermelon reveals the forward--inverse contrast, and the identifiability analysis provides the mathematical machinery. New computation required includes a forward-error-versus-inverse-conditioning figure, generalised rank-deficiency proofs for any scalar $g(a,c)$, curvature-sampling diagnostics per mode, and a cross-application classification table.

The working title --- \emph{Geometry Mediates Excitation, Resonance, and Identifiability in Fluid-Filled Viscoelastic Shells} --- doubles as the programme's one-sentence identity. The key insight, distilled: ``The joke was never the point. Geometry was.''

\subsection{Consolidation Priorities}

Three operational priorities follow from the Board's assessment:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Stop adding applications unless they test a conjecture.} The programme has sufficient breadth; what it needs is depth. New systems should be pursued only if they advance or test one of the four conjectures.
  \item \textbf{Seek one phantom collaboration.} A silicone oblate spheroidal phantom instrumented with laser vibrometry would provide the first external test of the analytical predictions, anchoring the programme in empirical reality.
  \item \textbf{Monograph after capstone, not before.} The temptation to write a monograph prematurely has been noted and resisted. The capstone must come first to establish the intellectual spine around which the full narrative can be organised.
\end{enumerate}

\section{Research Trajectory}

\subsection{Near-Term: Submission Wave}

Four papers are submission-ready: Paper~1 (JSV, $\sim$46\,pp.), Paper~2 (JASA, $\sim$18\,pp.), Paper~7 (Postharvest Biology and Technology, $\sim$32\,pp.), and Paper~8 (IPSE or JSV, $\sim$29\,pp.). Papers~3 and~4 require minor revisions. Papers~5 and~6 have passed the internal three-reviewer panel and await final formatting. The immediate priority is to begin the external peer review process across multiple venues simultaneously.

\subsection{Medium-Term: Consolidation and Validation}

The capstone synthesis paper (Paper~10) is the programme's central medium-term objective, with an estimated timeline of six to eight weeks to submission quality. In parallel, two experimental collaborations are being explored: an oblate spheroidal silicone phantom ($a = \SI{0.18}{\m}$, $c = \SI{0.12}{\m}$, $h = \SI{10}{\mm}$) to test the predicted $f_2 \approx \SI{4}{\Hz}$, and clinical bowel sound recordings from healthy subjects to test Paper~5's frequency predictions against measured spectra.

\subsection{Long-Term: From Programme to School}

The Advisory Board's ``obituary line'' for the programme reads: \emph{He began by asking whether the brown note existed, and ended by founding a general spectral mechanics of fluid-filled soft shells.} Achieving this requires three further steps: the capstone paper (establishing the mathematical core), at least one experimental validation (anchoring the theory in measurement), and a monograph (collecting the full programme into a coherent volume). The long-term applications --- non-invasive elastography, clinical bowel sound analysis, agricultural quality assessment, acoustic metamaterial analogies --- follow naturally from a validated framework, and need not be pursued until the theoretical foundations are secure.

\subsection{Doctoral Projects}

The programme generates at least three natural doctoral projects: (a)~experimental validation of the predicted modal spectrum using silicone oblate spheroidal phantoms instrumented with laser Doppler vibrometry; (b)~extension to non-oblate geometries --- prolate shells, irregular anatomies, and coupled multi-cavity systems --- testing the generality of the curvature-lifting mechanism; and (c)~computational inversion using clinical bowel sound recordings or watermelon tap-tone data, bridging the gap between analytical prediction and real-world measurement.

\subsection{Limitations}

The programme is purely analytical: no experimental validation has yet been performed, no finite-element modelling has been employed beyond mesh-convergence verification, and the framework has not been tested against irregular geometries or clinical data. These represent future work rather than present deficiencies --- the analytical foundations must be secure before experimental extension is meaningful.

\section{Broader Impact}

\subsection{From Folklore to Framework}

The programme demonstrates that folklore can seed rigorous science. The brown note hypothesis led to the first systematic analysis of abdominal vibroacoustic resonance, and thence to a ten-paper portfolio spanning cavity mechanics, clinical acoustics, agricultural diagnostics, and inverse identifiability theory. The lesson is not that folklore is reliable, but that the effort required to \emph{disprove} it rigorously often produces frameworks of independent value.

\subsection{Generalisable Framework}

The analytical toolchain is not specific to any single organ or fruit. Any fluid-filled cavity --- biological, agricultural, or industrial --- can be modelled within the same framework. The scaling laws provide principled extrapolation between species and systems. The identifiability analysis generalises to any inverse problem in which a forward model's geometric dependence passes through a low-dimensional proxy --- a structure common across biomedical imaging, non-destructive testing, and geophysical inversion.

\subsection{AI-Assisted Research as Method}

The programme is, to our knowledge, among the first to employ a structured multi-agent AI system as the primary research executor under human supervision. The infrastructure --- 24 agents, 22 skills, 92 research logs, and an open-source repository --- offers a replicable template for other research groups. The central insight is that AI's comparative advantage lies not in replacing scientific judgement but in \textbf{compressing the overhead} that separates a research idea from a publishable manuscript.

\section{Reflections on Process}

The read-to-write ratio across the system exceeds 1:1 --- the agents spend as much time inspecting and reviewing their own output as they do generating it. This is not an artefact; it was designed in.

\subsection{The $\sigma_\mathrm{abs}$ Story}

During Paper~1's seventh Reviewer~B round, a factor-of-four error was discovered in the Breit--Wigner absorption cross-section formula. This was not a typographical issue; it was a genuine physics bug that had propagated through the energy-consistent displacement calculation, affecting the coupling ratio and the airborne displacement estimates throughout the programme. Correcting it shifted $\xi_\mathrm{energy}$ from \SI{0.014}{\micro\m} to \SI{0.028}{\micro\m} and $\mathcal{R}$ from $6.6 \times 10^4$ to $3.3 \times 10^4$. The qualitative conclusions were unchanged --- airborne coupling remains negligible by any measure --- but the quantitative precision improved materially.

The episode illustrates two things. First, the adversarial review process works: an AI reviewer, given a clear mandate to find fatal flaws, identified a real error in the underlying physics that had survived multiple earlier rounds. Second, the correction \emph{strengthened} the programme's credibility rather than undermining it. By catching and correcting a factor-of-four error internally, the team demonstrated the same self-correcting rigour that external peer review is designed to provide.

\section{Selected Publications}

\begin{enumerate}[leftmargin=*]
  \item J.~Mace and B.\,R.~Mace, ``Modal Analysis of a Fluid-Filled Viscoelastic Oblate Spheroidal Shell: Implications for the Existence of the `Brown Note','' \emph{Journal of Sound and Vibration}, in preparation, 2026. ($\sim$46\,pp.)

  \item J.~Mace and B.\,R.~Mace, ``Bowel Gas as an Acoustic Transducer: A Constrained Bubble Model for Infrasound-Induced Mechanotransduction in the Gastrointestinal Tract,'' \emph{The Journal of the Acoustical Society of America}, in preparation, 2026. ($\sim$18\,pp.)

  \item J.~Mace and B.\,R.~Mace, ``Scaling Laws for the Flexural Resonance of Fluid-Filled Viscoelastic Shells: Predictions Across Mammalian Scales,'' \emph{Journal of Sound and Vibration --- Short Communication}, in preparation, 2026. ($\sim$8\,pp.)

  \item J.~Mace and B.\,R.~Mace, ``Resonant Frequencies of the Human Urinary Bladder: A Fluid-Filled Viscoelastic Shell Model,'' \emph{Journal of Sound and Vibration}, in preparation, 2026. ($\sim$27\,pp.)

  \item J.~Mace and B.\,R.~Mace, ``What Pitch Is a Growling Stomach? A Unified Multi-Mode Acoustic Model of Borborygmi,'' \emph{The Journal of the Acoustical Society of America}, in preparation, 2026. ($\sim$20\,pp.)

  \item J.~Mace and B.\,R.~Mace, ``Can You Feel the Bass? Quantitative Partition of Airborne and Structure-Borne Pathways for Sub-Bass Perception at Concert Sound Pressure Levels,'' \emph{The Journal of the Acoustical Society of America}, in preparation, 2026. ($\sim$18\,pp.)

  \item J.~Mace and B.\,R.~Mace, ``Can You Hear the Ripeness? Non-Destructive Acoustic Assessment of Fruit Maturity via Equivalent-Sphere Shell Resonance Inversion,'' \emph{Postharvest Biology and Technology}, in preparation, 2026. ($\sim$32\,pp.)

  \item J.~Mace and B.\,R.~Mace, ``Can You Hear the Shape of an Organ? Practical Identifiability of Viscoelastic Shell Parameters from Resonant Frequencies,'' \emph{Inverse Problems in Science and Engineering}, in preparation, 2026. ($\sim$29\,pp.)

  \item J.~Mace and B.\,R.~Mace, ``On the Curvature-Lifting Mechanism in Fluid-Filled Shell Inversion,'' \emph{Journal of Sound and Vibration --- Short Communication}, in preparation, 2026.

  \item J.~Mace and B.\,R.~Mace, ``Geometry Mediates Excitation, Resonance, and Identifiability in Fluid-Filled Viscoelastic Shells,'' \emph{Proceedings of the Royal Society~A}, in preparation, 2026. (scaffolded)
\end{enumerate}

\vfill
\begin{center}
  \small\itshape Prepared March 2026. Browntone Research Lab, Microsoft Research / University of Auckland.
\end{center}

\end{document}
