\documentclass[review]{elsarticle}

% =============================================================================
% Packages
% =============================================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{lineno}

% Fix duplicate page destination warning with elsarticle review mode
\hypersetup{pageanchor=false}
\AtBeginDocument{\hypersetup{pageanchor=true}}

% SI units configuration
\sisetup{
  per-mode=symbol,
  group-separator={,},
}

% Line numbering (required for JSV review submission)
\linenumbers

% =============================================================================
% Metadata
% =============================================================================
\journal{Journal of Sound and Vibration}

\begin{document}

\begin{frontmatter}

\title{Modal Analysis of a Fluid-Filled Viscoelastic Oblate Spheroidal Shell:
Implications for the Existence of the ``Brown Note''}

\author[msr]{Jonathan Mace\corref{cor1}}
\cortext[cor1]{Corresponding author}
\ead{jonathanmace@microsoft.com}

\author[auckland]{Brian R.\ Mace}
\ead{br.mace@auckland.ac.nz}

\author[springbank]{Springbank 10 Year Old\fnref{fn1}}
\fntext[fn1]{Non-sentient author. Contribution limited to inspiration, courage,
  and a pleasantly peaty finish. The distillery neither endorses nor is aware of
  this work.}

\author[github]{GitHub Copilot CLI\fnref{fn2}}
\fntext[fn2]{Large language model. Performed literature review, analytical
  computation, code development, figure generation, and manuscript drafting
  under human supervision.}

\affiliation[msr]{
  organization={Microsoft Research},
  city={Redmond, WA},
  country={United States}
}

\affiliation[auckland]{
  organization={Acoustics Research Centre, Department of Mechanical and
    Mechatronics Engineering, University of Auckland},
  city={Auckland},
  country={New Zealand}
}

\affiliation[springbank]{
  organization={Springbank Distillery},
  city={Campbeltown, Argyll},
  country={Scotland}
}

\affiliation[github]{
  organization={GitHub, Inc.},
  city={San Francisco, CA},
  country={United States}
}

\begin{highlights}
\item Mechanical--airborne coupling disparity of $\sim$$10^4$ explains gastrointestinal vibration asymmetry
\item Fluid-filled viscoelastic shell model predicts abdominal resonance at 4--10 Hz (matches ISO~2631)
\item Breathing mode at $\sim$2500 Hz; flexural modes at infrasonic frequencies
\item Airborne coupling penalised by $(ka)^n$; negligible at 120 dB SPL ($\xi = \SI{0.014}{\micro\metre}$)
\item Monte Carlo UQ confirms robustness; Sobol $S_T = 0.86$ for elastic modulus
\end{highlights}

\begin{abstract}
Whole-body vibration at \SIrange{4}{8}{\hertz} causes well-documented
gastrointestinal disturbances, yet airborne sound at the same frequencies does
not---even at extreme intensities.  We resolve this long-standing asymmetry
by modelling the human abdomen as a fluid-filled viscoelastic oblate
spheroidal shell and quantifying the coupling efficiency of both excitation
pathways within a common energy-budget framework.

The model reveals two distinct mode families.  The breathing mode ($n=0$),
dominated by the fluid bulk modulus, sits near \SI{2500}{\hertz} and is
irrelevant at infrasonic frequencies.  Flexural modes ($n \geq 2$), in which
the shell deforms without compressing the enclosed fluid, fall in the
\SIrange{4}{10}{\hertz} range for relaxed musculature---consistent with
abdominal resonance data from ISO~2631.  At these frequencies, however, the
acoustic wavelength exceeds \SI{49}{\metre}, placing the abdomen deep in the
Rayleigh regime ($ka \approx 0.01$).  The resulting $(ka)^n$ geometric
penalty, compounded by the air--tissue impedance mismatch, reduces airborne
coupling by approximately four orders of magnitude.  Energy-consistent
analysis yields wall displacements of \SI{0.014}{\micro\metre} at
\SI{120}{\decibel} SPL---far below known mechanotransduction thresholds.
Mechanical vibration, transmitted through the skeleton, suffers neither penalty
and produces displacements roughly $4.6 \times 10^4$ times larger at
occupational exposure levels.  Monte Carlo uncertainty quantification confirms
this coupling disparity across physiologically realistic parameter ranges
(Sobol $S_T = 0.86$ for elastic modulus).

The result explains the empirical record quantitatively and, incidentally,
settles the ``brown note'' question: the abdominal resonance invoked by the
myth is genuine, but airborne sound is the wrong mechanism by four orders of
magnitude.
\end{abstract}

\begin{keyword}
fluid-filled shell vibration \sep viscoelastic oblate spheroid \sep
infrasound \sep whole-body vibration \sep acoustic--structural coupling \sep
ISO~2631
\end{keyword}

\end{frontmatter}

% =============================================================================
% Section 1: Introduction
% =============================================================================
\input{sections/introduction}

% =============================================================================
% Section 2: Mathematical Formulation (the core contribution)
% =============================================================================
\input{sections/section2_formulation}

% =============================================================================
% Section 3: Parametric Study
% =============================================================================
\input{sections/results}

% =============================================================================
% Section 4: Coupling Comparison (key novel result)
% =============================================================================
\input{sections/section4_coupling}

% =============================================================================
% Section 5: Discussion
% =============================================================================
\input{sections/discussion}

% =============================================================================
% Section 6: Conclusions
% =============================================================================
\input{sections/conclusion}

% =============================================================================
% References
% =============================================================================
\bibliographystyle{elsarticle-num}
\bibliography{references}

% =============================================================================
% Data Availability & CRediT
% =============================================================================
\section*{Data availability}
All analytical models and computational scripts used in this study are
available in the accompanying repository.

\section*{CRediT authorship contribution statement}
\textbf{Jonathan Mace}: Conceptualization, Methodology, Supervision,
Writing -- Review \& Editing.
\textbf{Brian R.\ Mace}: Writing -- Review \& Editing, Validation.
\textbf{Springbank 10 Year Old}: Morale, Inspiration.  (A single-malt
Scotch whisky from Campbeltown.  Its contribution, while not strictly
peer-reviewable, was essential to sustaining the authors through the
less glamorous phases of manuscript preparation.)
\textbf{GitHub Copilot CLI}: Software, Formal Analysis, Investigation,
Data Curation, Writing -- Original Draft, Visualization.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests
or personal relationships that could have appeared to influence the work
reported in this paper.

\end{document}
