% =============================================================================
% Conclusion
% =============================================================================
\section{Conclusion}\label{sec:conclusion}

We have studied the practical identifiability of viscoelastic shell parameters
from resonant frequencies in the spirit of Kac's spectral question.  For the
equivalent-sphere flexural model used here, the inverse problem based on the
parameter triple $(a,c,E)$ is almost singular at the spherical operating point
but well conditioned at the canonical oblate operating point.

The main findings are:
\begin{enumerate}
  \item the spherical Jacobian is effectively rank deficient, with
  $\kappa = 1.1 \times 10^{10}$;
  \item the oblate Jacobian is well conditioned, with $\kappa = 73.0$;
  \item the improvement factor is approximately $1.5 \times 10^{8}$;
  \item local round-trip inversion recovers $(a,c,E)$ to relative errors below
  $10^{-12}$;
  \item at $1\%$ frequency noise, the Cram\'er--Rao bounds are approximately
  $\pm 37\%$ for $a$, $\pm 13\%$ for $c$, and $\pm 36\%$ for $E$;
  \item three-mode inversion is vulnerable to local minima, whereas five-mode
  inversion is robust across the tested initial guesses;
  \item a ripe-watermelon case remains well conditioned, with
  $\kappa \approx 104$.
\end{enumerate}

These results suggest a practical answer to the question posed in the title.
Within the present model, one can hear the shape of an oblate organ in the
limited but useful sense of practical local identifiability.  One cannot do so
reliably at the spherical limit.

The clearest practical recommendation is straightforward: measure at least five
low-order flexural resonances if the goal is parameter inversion rather than
mere modal description.  Fewer modes may suffice for local tests, but they do
not provide the same robustness.

Future work should replace the equivalent-sphere approximation by a true oblate
Ritz model with explicit aspect-ratio dependence, and should test the inversion
experimentally on phantoms and biological specimens.  That would move the
present study from ``practically identifiable in silico'' to ``experimentally
recoverable in the laboratory'', which is a more demanding and more interesting
standard.
