% =============================================================================
% Discussion
% =============================================================================
\section{Discussion}\label{sec:discussion}

\subsection{Connection to Kac's question}

Kac's original problem asked whether one could infer geometry from a spectrum.
Our answer is deliberately narrower and more practical.  For the present
viscoelastic shell model, the results suggest that one \emph{can} hear the shape
of an oblate organ, in the sense that the local inverse problem for
$(a,c,E)$ is well conditioned and statistically finite.  At the spherical
limit, one cannot: the Jacobian becomes rank deficient and the Fisher matrix
loses invertibility.

The analogy with Kac should therefore be handled with care.  We do not prove a
uniqueness theorem over an infinite function space, nor do we exclude the
possibility of remote isospectral parameter sets.  Our claim is about
\emph{practical identifiability} in a finite-dimensional model relevant to
measurement and inversion.  That is a less grand claim, but also the one an
experimentalist can actually use.

\subsection{Implications for vibroacoustic elastography}

The results are encouraging for vibroacoustic elastography and related spectral
methods.  A small number of low-order flexural resonances may contain enough
information to estimate both geometry and stiffness, provided that the operating
point is sufficiently aspherical and provided that enough modes are measured.
This is attractive because resonant frequencies are often easier to estimate
robustly than full-field mode shapes or transient wavefields.

The Cram\'er--Rao bounds give the result practical content.  At $1\%$ frequency
noise, the uncertainty in $c$ is modest, while $a$ and $E$ remain more weakly
resolved but still finite.  That anisotropy matters for experimental design:
one should not expect the same confidence in all parameters, even when the
Jacobian has full rank.

\subsection{Why model choice matters}

The most important modelling lesson is that forward-model convenience and
inverse-model usefulness are not the same thing.  A spherical reduction may be
acceptable for a rough forward estimate of resonance frequency, but it is a poor
foundation for parameter recovery.  Spherical simplifications are serviceable on
the blackboard; in inverse problems they become noticeably less cooperative.

At the same time, the present study does \emph{not} rely on a full oblate shell
theory.  The model analysed here is still an equivalent-sphere approximation.
That limitation should be kept in view when interpreting the phrase ``hear the
shape''.  The present results show what is identifiable within the implemented
model, not what Nature has promised in advance.

\subsection{Relation to existing inverse methods}

Inverse vibration problems have long been studied in structural
dynamics~\cite{Gladwell2004,Gladwell2005}, and model-based elastography has
developed a wide range of optimisation and regularisation
strategies~\cite{Doyley2012}.  In acoustics and biomechanics, several studies
have estimated material parameters by fitting dynamic response models to
spectral data~\cite{Aernouts2012}.  The present contribution is more modest but
useful: before attempting a sophisticated inversion, we ask whether the chosen
measurements can, in principle, resolve the chosen parameters with acceptable
conditioning.

That perspective is valuable because poor inverse performance is often blamed on
optimisers, priors, or noise models when the underlying issue is simpler: the
Jacobian is nearly singular.  A condition-number and Fisher-information analysis
cannot solve the inverse problem by itself, but it can prevent one from asking
the data for information they do not contain.

\subsection{Local versus global identifiability}

The round-trip tests demonstrate very accurate local recovery, but global
identifiability is a separate matter.  The three-mode system is especially
vulnerable because it is exactly determined.  Local minima can occur, and a
small residual does not necessarily imply the correct parameter set when the
search is started far away.  This is why the five-mode result matters more for
practice than the machine-precision local recovery.

Our recommendation is therefore not based on elegance but on behaviour:
\begin{itemize}
  \item use three modes only for local studies or controlled round-trip tests;
  \item use at least five flexural modes for robust inversion in realistic
  settings.
\end{itemize}

\subsection{Limitations}

Several limitations remain.
\begin{enumerate}
  \item The forward model is an equivalent-sphere approximation.  It does not
  contain explicit $\zeta_g$-dependent shell terms, so the present paper should
  not be read as a definitive study of full spheroidal shell identifiability.
  \item The analysis is local.  We do not prove global injectivity of the map
  $(a,c,E)\mapsto \{f_n\}$.
  \item Synthetic inversion uses the same model for data generation and
  inversion.  This isolates identifiability, but it avoids model-form error.
  \item The mode numbers are assumed known.  In experiment, mode assignment may
  itself be uncertain.
  \item Only three parameters are estimated.  Allowing $h$, $\nu$, or fluid
  properties to vary would enlarge the parameter space and may degrade
  conditioning.
\end{enumerate}

\subsection{Future directions}

The natural next step is a genuine Ritz or finite-element oblate shell model
with explicit aspect-ratio dependence, followed by the same identifiability
analysis.  That would show whether the encouraging results reported here
strengthen further when the geometry is represented more faithfully.  The second
priority is experimental validation, ideally first on phantoms of known
geometry and stiffness and then on biological specimens.  A Bayesian treatment,
with priors on tissue properties and uncertainty in mode identification, would
also be a useful extension.
