% =============================================================================
% Results
% =============================================================================
\section{Results}\label{sec:results}

\subsection{Headline identifiability contrast}

The principal result is the contrast between the spherical and oblate operating
points.  Using the scaled Jacobian built from the flexural modes
$n=2,\ldots,6$, the spherical case gives
\begin{equation}
  \kappa_\mathrm{sphere} = 1.1 \times 10^{10},
\end{equation}
whereas the canonical oblate case gives
\begin{equation}
  \kappa_\mathrm{oblate} = 73.0.
\end{equation}
The corresponding improvement factor is therefore
\begin{equation}
  \frac{\kappa_\mathrm{sphere}}{\kappa_\mathrm{oblate}}
  \approx 1.5 \times 10^{8}.
\end{equation}
By the standards of practical inversion, this is the difference between an
essentially singular map and a well-conditioned three-parameter estimate.

\subsection{Singular-value structure}

The singular value decomposition provides the clearest picture.  In the
spherical case, one singular value collapses to a value near machine zero,
leaving one parameter combination effectively unobservable.  In the oblate
case, all three singular values remain finite and well separated from zero.
The spectrum therefore spans the three-dimensional parameter space
$(a,c,E)$ locally.

This observation is more informative than the condition number alone.  A large
$\kappa$ could arise from one weak direction in an otherwise healthy problem; in
the spherical case, the singular values show something stronger: the Jacobian is
numerically rank deficient.  At the oblate operating point, by contrast, the
inverse map is not perfect but it is usable.

\subsection{Physical interpretation}

The implemented forward model contains no explicit aspect-ratio terms; it is an
equivalent-sphere model parameterised through
$R_\mathrm{eq}=(a^2c)^{1/3}$.  The numerical results should therefore be read
accordingly.  We are not claiming that explicit spheroidal curvature terms have
been identified in the inverse map.  Rather, the results suggest that, within
this model, the modal balance of bending
($K_\mathrm{bend}^{(n)} \propto R_\mathrm{eq}^{-4}$), membrane
($K_\mathrm{memb}^{(n)} \propto R_\mathrm{eq}^{-2}$), prestress
($K_\mathrm{pre}^{(n)} \propto R_\mathrm{eq}^{-1}$), and added mass
($m_\mathrm{eff}^{(n)} = \rho_w h + \rho_f R_\mathrm{eq}/n$) varies
sufficiently with mode number to separate the sensitivity directions away from
the spherical limit.

For the spherical operating point, those sensitivities collapse onto a nearly
degenerate pattern: geometry and stiffness become strongly confounded, and the
smallest singular value tends to zero.  For the oblate operating point, the
same confounding is greatly reduced.  The result is numerical rather than
theorematic, but it is robust across the tested cases.

\subsection{Round-trip inversion}

Round-trip inversion confirms the local picture.  When synthetic frequencies are
generated by the forward model and the solver is initialised within the local
basin of attraction, the recovered parameters satisfy
\begin{equation}
  \frac{|\hat a-a|}{a},
  \frac{|\hat c-c|}{c},
  \frac{|\hat E-E|}{E}
  < 10^{-12}.
\end{equation}
This is essentially machine-precision recovery of the original parameter set.

The distinction between local and global behaviour is important.  With only
three modes, the inverse problem is exactly determined and the solver can
encounter local minima or alternative low-residual basins.  With five modes
($n=2,\ldots,6$), the system becomes overdetermined and the same inversion is
globally robust across the tested perturbations of the initial guess.  The
results therefore support a clear experimental design rule: three modes may be
enough to tempt the optimiser, but five modes are what persuade it to behave.

\subsection{Cram\'er--Rao bounds}

Table~\ref{tab:crlb} summarises the Cram\'er--Rao lower bounds for the canonical
oblate case at $1\%$ frequency noise.  The smallest uncertainty is obtained for
$c$, whereas $a$ and $E$ are comparably less well constrained.

\begin{table}[t]
  \centering
  \caption{Cram\'er--Rao lower bounds for the canonical oblate case at
  $1\%$ fractional frequency noise.  Relative bounds are reported as one
  standard deviation.}
  \label{tab:crlb}
  \begin{tabular}{lccc}
    \toprule
    Parameter & Nominal value & Absolute bound & Relative bound \\
    \midrule
    $a$ & \SI{0.18}{m}    & $\pm\,\SI{0.067}{m}$   & $\pm\,37\%$ \\
    $c$ & \SI{0.12}{m}    & $\pm\,\SI{0.016}{m}$   & $\pm\,13\%$ \\
    $E$ & \SI{0.1}{MPa}   & $\pm\,\SI{0.036}{MPa}$ & $\pm\,36\%$ \\
    \bottomrule
  \end{tabular}
\end{table}

For the spherical case, the Fisher matrix is singular and no finite
Cram\'er--Rao bound exists in the degenerate direction.  This is the statistical
counterpart of the singular-value result: the data simply do not contain enough
independent information at that operating point.

As expected from \eqref{eq:fisher}, the bounds scale linearly with noise level.
Halving the frequency noise from $2\%$ to $1\%$ halves the minimum-achievable
parameter standard deviations.  The uncertainty budget is therefore governed by
two levers: the intrinsic conditioning of the operating point and the
experimental precision of the measured resonances.

\subsection{Condition-number map in parameter space}

Condition-number maps over $(a,\zeta_g)$ show a broad region of acceptable
conditioning across physiologically relevant oblate geometries.  The condition
number increases steadily as $\zeta_g \rightarrow 0$, that is, as the geometry
approaches a sphere.  This trend is physically and numerically consistent with
the singular spherical limit.  Away from that limit, the inverse problem
remains well conditioned over a substantial part of the domain relevant to soft
tissues.

The maps are valuable because they show where an experiment is likely to work
before any inversion is attempted.  They also suggest that identifiability is
not a single number attached to the model in general; it depends strongly on the
operating point.

\subsection{Watermelon cross-application}

The same analysis applied to a ripe watermelon gives
\begin{equation}
  \kappa \approx 104.
\end{equation}
This value is somewhat worse than the canonical abdomen, but it is still well
within the range of practical inversion.  The result shows that the underlying
identifiability mechanism is not confined to one biological parameter set.

The watermelon case also helps separate geometry from scale.  The stiffness is
orders of magnitude larger than in soft tissue, yet the inverse problem remains
tractable.  The conditioning therefore reflects the structure of the
frequency--parameter map rather than a peculiarity of one very soft shell.
