% =============================================================================
% Theory
% =============================================================================
\section{Theory}\label{sec:theory}

\subsection{Equivalent-sphere forward model}

We use the flexural-frequency model introduced in the companion
paper~\cite{BrowntoneCompanion}.  The shell has semi-major axis $a$, semi-minor
axis $c$, thickness $h$, Young's modulus $E$, Poisson's ratio $\nu$, wall
density $\rho_w$, and internal fluid density $\rho_f$.  The fluid bulk modulus
is denoted by $K_f$, the static internal pressure by $P_\mathrm{iap}$, and the
loss tangent by $\eta$.  Unless stated otherwise, the canonical parameter set is
\[
a=\SI{0.18}{m},\quad
c=\SI{0.12}{m},\quad
h=\SI{0.01}{m},\quad
E=\SI{0.1}{MPa},\quad
\nu=0.45,
\]
\[
\rho_w=\SI{1100}{kg/m^3},\quad
\rho_f=\SI{1020}{kg/m^3},\quad
K_f=\SI{2.2}{GPa},\quad
P_\mathrm{iap}=\SI{1000}{Pa},\quad
\eta=0.25.
\]

The model collapses the geometry to the equivalent radius
\begin{equation}\label{eq:req}
  R_\mathrm{eq} = (a^2 c)^{1/3}.
\end{equation}
For flexural modes $n \geq 2$, the angular frequency $\omega_n=2\pi f_n$ is
written as
\begin{equation}\label{eq:flexural_forward}
  \omega_n^2
  =
  \frac{K_\mathrm{bend}^{(n)} + K_\mathrm{memb}^{(n)} + K_\mathrm{pre}^{(n)}}
       {m_\mathrm{eff}^{(n)}},
\end{equation}
where the effective stiffness contains bending, membrane, and prestress terms,
and the effective mass contains wall mass and fluid added mass.

With flexural rigidity
\begin{equation}
  D = \frac{E h^3}{12(1-\nu^2)},
\end{equation}
the individual contributions are
\begin{equation}
  K_\mathrm{bend}^{(n)}
  =
  \frac{n(n-1)(n+2)^2}{R_\mathrm{eq}^4}\,D,
\end{equation}
\begin{equation}
  K_\mathrm{memb}^{(n)}
  =
  \frac{E h}{R_\mathrm{eq}^2}\,\lambda_n,
  \qquad
  \lambda_n
  =
  \frac{n^2+n-2+2\nu}{n^2+n+1-\nu},
\end{equation}
\begin{equation}
  K_\mathrm{pre}^{(n)}
  =
  \frac{P_\mathrm{iap}}{R_\mathrm{eq}}(n-1)(n+2),
\end{equation}
and
\begin{equation}
  m_\mathrm{eff}^{(n)}
  =
  \rho_w h + \frac{\rho_f R_\mathrm{eq}}{n}.
\end{equation}

Equation~\eqref{eq:flexural_forward} is the model analysed throughout this
paper.  It is important to emphasise again that it is \emph{not} a full oblate
spheroidal shell theory: explicit aspect-ratio terms do not appear.  The model
depends on $(a,c)$ only through $R_\mathrm{eq}$.

\subsection{Inverse problem}

Let
\begin{equation}
  \boldsymbol{\theta} = (a,c,E)^\top
\end{equation}
denote the parameter vector to be estimated, and let
\begin{equation}
  \mathbf{f}(\boldsymbol{\theta})
  =
  \bigl(f_2(\boldsymbol{\theta}),
        f_3(\boldsymbol{\theta}),
        \ldots,
        f_N(\boldsymbol{\theta})\bigr)^\top
\end{equation}
be the vector of measured flexural frequencies.  The inverse problem is to
recover $\boldsymbol{\theta}$ from the observation
$\mathbf{f}^\mathrm{obs}$.

Local identifiability is controlled by the Jacobian
\begin{equation}\label{eq:jacobian_raw}
  J_{ij}
  =
  \frac{\partial f_i}{\partial \theta_j},
\end{equation}
where $i$ indexes the measured mode and $j$ indexes the unknown parameter.
Because the raw Jacobian mixes units of \si{Hz/m} and \si{Hz/Pa}, its condition
number is not a meaningful identifiability metric by itself.  We therefore use
the dimensionless scaled Jacobian
\begin{equation}\label{eq:jacobian_scaled}
  J_s[i,j]
  =
  \left(\frac{\partial f_i}{\partial \theta_j}\right)
  \left(\frac{\theta_j}{f_i}\right),
\end{equation}
which measures fractional frequency change per fractional parameter change.

The singular values $\sigma_1 \ge \sigma_2 \ge \sigma_3$ of $\mathbf{J}_s$
quantify the observable directions in parameter space, and the corresponding
condition number
\begin{equation}\label{eq:kappa}
  \kappa(\mathbf{J}_s)
  =
  \frac{\sigma_{\max}}{\sigma_{\min}}
\end{equation}
measures the worst-case amplification of small frequency errors into parameter
errors.  A large $\kappa$ indicates a nearly unobservable parameter
combination; a divergent $\kappa$ indicates rank deficiency.

\subsection{Fisher information and Cram\'er--Rao bounds}

Assume independent fractional frequency errors with standard deviation
$\epsilon_\mathrm{noise}$.  In dimensionless form, the Fisher information
matrix becomes
\begin{equation}\label{eq:fisher}
  \mathbf{F}
  =
  \frac{1}{\epsilon_\mathrm{noise}^2}\,
  \mathbf{J}_s^\top \mathbf{J}_s.
\end{equation}
Equivalently, one may interpret \eqref{eq:fisher} as the Fisher matrix of the
whitened residuals.  The Cram\'er--Rao lower bound then states that the
covariance of any unbiased local estimator satisfies
\begin{equation}\label{eq:crlb}
  \mathrm{Cov}(\hat{\boldsymbol{\theta}})
  \succeq
  \mathbf{F}^{-1},
\end{equation}
with the diagonal entries of $\mathbf{F}^{-1}$ giving the minimum achievable
variances under the assumed noise model.

This framework does not prove global uniqueness.  It answers a more practical
question: at a chosen operating point, do the measured resonances contain enough
independent information to recover $(a,c,E)$ with tolerable sensitivity to
noise?  That is the question addressed in the next sections.
